### 2019-03-26 abstract/abstract.tex
Add in abstract shell with sections

%        File: abstract.tex
%     Created: Tue Mar 26 06:00 AM 2019 E
% Last Change: Tue Mar 26 06:00 AM 2019 E
%
\documentclass{article}
\begin{document}

\title{CS287 Final Project Abstract}
\author{Francisco Rivera \and Jiafeng (Kevin) Chen \and Yufeng Ling}
\date{\today}

\maketitle

\section{Area}

% TODO: write up area

\section{Papers}

% TODO: bring in the two papers and find a third

\section{Time}

We have already signed up for Monday April 22.

\section{Baseline}

% TODO: this is the hardest thing we need to decide

\end{document}

### 2019-03-27 abstract/abstract.tex
Add in paper citations
New bibliography style and tex macros
Finished writing abstract; still need literature

@@
 %
-\documentclass{article}
+\documentclass[11pt]{article}
+\usepackage{macros}
 \begin{document}
@@
 \title{CS287 Final Project Abstract}
-\author{Francisco Rivera \and Jiafeng (Kevin) Chen \and Yufeng Ling}
+\author{Francisco Rivera\thanks{\texttt{frivera@college.harvard.edu}} \and Jiafeng (Kevin) Chen\thanks{\texttt{jiafengchen@college.harvard.edu}} \and Yufeng Ling\thanks{\texttt{yufengling@college.harvard.edu}}}
 \date{\today}
@@
 
+Variational autoencoders (VAE) are a powerful method for learning latent
+representations of high-dimensional objects; these representations preserve the
+underlying structure of the objects, and have useful features such as
+interpolation and natural clustering. In vector-quantized VAE (VQ-VAE), we
+discretize the representation space, using the vector quantization algorithm.
+Discretizing the representation space effectively compresses inputs, and in some
+cases, may lead to interpretable discrete latent codes. We are interested in
+using recent advances in vector-quantized variational autoencoding (VQ-VAE) to
+improve machine translation, particularly in low-resource settings.
+
+VQ-VAE has
+been used \citep{kaiser2018fast} to speed up machine translation. VQ-VAE
+achieves this by compressing sentences into shorter discrete representations,
+which are then translated using a encoder--decoder framework (e.g. transformer).
+The speedup is provided since the variational encoding and decoding parts are
+parallelizable. We anticipate that VQ-VAE may also be helpful in low-resource
+settings, since variational autoencoding is unsupervised. In particular, recent
+advances in VQ-VAE has shown that it can style transfer audio into being spoken
+by different
+speakers, in a fully unsupervised manner \citep{van2017neural}. Speaker style
+transfer is a task that
+bears some similarities to translation, and we hope to
+leverage these recent advances for low-resource machine translation.
 % TODO: write up area
@@
 \section{Papers}
+\begin{itemize}
+    \item Our main paper is \cite*{van2017neural}, which introduces VQ-VAE.
+    VQ-VAE differs from traditional VAEs in two crucial aspects: (1) VQ-VAE is
+    discrete, and (2) the prior is learned. 
+    \item \cite*{kaiser2018fast}  
+    \item \cite{guzman2019two}
+\end{itemize}
 
@@
 
+\bibliographystyle{ecca}
+\bibliography{sources}
+
 \end{document}

### 2019-03-27 abstract/abstract.tex
added baseline

@@
 
-% TODO: bring in the two papers and find a third
-
 \section{Time}
@@
 
-% TODO: this is the hardest thing we need to decide
+We will be using the same Nepali-English and Sinhala-English datasets as in \cite{guzman2019two}.
+Those languages are only spoken by less than 20 million people in Nepal and Sri Lanka respectively.
+They are categorized by small amount out-of-domain parallel data and large amount of monolingual data.
+
+With very limited supervised dataset ($\sim$ 500K sentences), the paper achieved BLEU scores of less than 8 for Nepali and Sinhala to English.
+With a combination of supervised translation data and monolingual data on the target side, BLEU scores increased to 15.1 for both.
+Finally, unsupervised learning generated BLEU score very close to 0.
+We intend to use those as baseline and improve upon them.
 

### 2019-03-27 abstract/abstract.tex
Changes to abstract

@@
 
-VQ-VAE has
-been used \citep{kaiser2018fast} to speed up machine translation. VQ-VAE
-achieves this by compressing sentences into shorter discrete representations,
-which are then translated using a encoder--decoder framework (e.g. transformer).
-The speedup is provided since the variational encoding and decoding parts are
-parallelizable. We anticipate that VQ-VAE may also be helpful in low-resource
-settings, since variational autoencoding is unsupervised. In particular, recent
-advances in VQ-VAE has shown that it can style transfer audio into being spoken
-by different
-speakers, in a fully unsupervised manner \citep{van2017neural}. Speaker style
-transfer is a task that
-bears some similarities to translation, and we hope to
-leverage these recent advances for low-resource machine translation.
-% TODO: write up area
+VQ-VAE has been used \citep{kaiser2018fast} to speed up machine translation.
+VQ-VAE achieves this by compressing sentences into shorter discrete
+representations, which are then translated using a encoder--decoder framework
+(e.g. transformer). The speedup is provided since the variational encoding and
+decoding parts are parallelizable. We anticipate that VQ-VAE may also be helpful
+in low-resource settings, since variational autoencoding is unsupervised. In
+particular, recent advances in VQ-VAE has shown that it can style transfer audio
+into being spoken by different speakers, in a fully unsupervised manner
+\citep{van2017neural}. Speaker style transfer is a task that bears some
+similarities to translation, and we hope to leverage these recent advances for
+low-resource machine translation.% TODO: write up area
 

### 2019-05-10 paper/paper.tex
Merging from refactor-run-classifiers branch and adding paper skeleton

\documentclass{article}

\usepackage{times}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{natbib}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{lipsum}
\usepackage{todonotes}
\usepackage[accepted]{icml2017}

\usepackage{macros}

\icmltitlerunning{CS 287 Final Project Template}

\begin{document}

\twocolumn[
\icmltitle{BERT Model Compression and Weight Sharing}
\begin{icmlauthorlist}
  \icmlauthor{Jiafeng Chen}{}
\icmlauthor{Yufeng Ling}{}
\icmlauthor{Francisco Rivera}{}
\end{icmlauthorlist}

\vskip 0.3in
]

\begin{abstract}
  \begin{itemize}
  \item This document describes the expected style, structure, and rough proportions for your final project write-up.
  \item While you are free to break from this structure, consider it a strong prior for our expectations of the final report.
\item Length is a hard constraint. You are only allowed max \textbf{8 pages} in this format. While you can include supplementary material, it will not be factored into the grading process. It is your responsibility to convey the main contributions of the work in the length given.
  \end{itemize}

\end{abstract}

\section{Introduction}
\label{sec:introduction}

Example Structure:
\begin{itemize}
\item What is the problem of interest and what (high-level) are the current best methods for solving it?
\item How do you plan to improve/understand/modify this or related methods?
\item Preview your research process, list the contributions you made, and summarize your experimental findings.
\end{itemize}

\section{Background}
Example Structure:
\begin{itemize}
\item What information does a non-expert need to know about the problem domain?
\item What data exists for this problem?
\item What are the challenges/opportunities inherent to the data? (High dimensional, sparse, missing data, noise, structure, discrete/continuous, etc?)
\end{itemize}

\section{Related Work}

Example Structure:
\begin{itemize}
\item What 3-5 papers have been published in this space?
\item How do these  differ from your approach?
\item What data or methodologies do each of these works use?
\item How do you plan to compare to these methods?
\end{itemize}

\section{Model}

Example Structure:

\begin{itemize}
\item What is the formal definition of your problem?
\item What is the precise mathematical model you are using to represent it? In almost all cases this will use the probabilistic language from class, e.g.
  \begin{equation}
  z \sim {\cal N}(0, \sigma^2)\label{eq:1}
\end{equation}
But it may also be a neural network, or a non-probabilistic loss,
\[ h_t \gets \mathrm{RNN}(x_{t}, h_{t-1} )\]

This is also a good place to reference a diagram such as Figure~\ref{fig:diagram}.

\item What are the parameters or latent variables of this model that you plan on estimating or inferring? Be explicit. How many are there? Which are you assuming are given? How do these relate to the original problem description?
\end{itemize}

\begin{figure}
  \centering
  \missingfigure[figheight=8cm]{}
  \caption{\label{fig:diagram} This is a good place to include a diagram showing how your model works. Examples include a graphical model or a neural network block diagram.}
\end{figure}

\section{Inference (or Training)}

\begin{itemize}
\item How do you plan on training your parameters / inferring the
  states of your latent variables (MLE / MAP / Backprop / VI / EM / BP / ...)

\item What are the assumptions implicit in this technique? Is it an approximation or exact? If it is an approximation what bound does it optimize?

\item What is the explicit method / algorithm that you derive for learning these parameters?
\end{itemize}

\begin{algorithm}
  \begin{algorithmic}
    \STATE{}
  \end{algorithmic}
  \caption{Your Pseudocode}
\end{algorithm}

\section{Methods}

\begin{itemize}
\item What are the exact details of the dataset that you used? (Number of data points / standard or non-standard / synthetic or real / exact form of the data)

\item What are the exact details of the features you computed?

\item How did you train or run inference? (Optimization method / hyperparameter settings / amount of time ran / what did you implement versus borrow / how were baselines computed).

\item What are the exact details of the metric used?
\end{itemize}

\section{Results}

\begin{itemize}
\item What were the results comparing previous work / baseline systems / your systems on the main task?
\item What were the secondary results comparing the variants of your system?
\item This section should be fact based and relatively dry. What happened, what was significant?
\end{itemize}

\begin{table*}
  \centering
  \missingfigure{}
  \caption{This is usually a table. Tables with numbers are generally easier to read than graphs, so prefer when possible.}
  \label{fig:mainres}
\end{table*}

\begin{table}
  \centering
  \missingfigure[figheight=5cm]{}
  \caption{Secondary table or figure in results section.}
  \label{fig:mainres}
\end{table}

\section{Discussion}

\begin{itemize}
\item What conclusions can you draw from the results section?
\item Is there further analysis you can do into the results of the system? Here is a good place to include visualizations, graphs, qualitative analysis of your results.

\item  What questions remain open? What did you think might work, but did not?
\end{itemize}

\begin{figure}
  \centering
  \missingfigure{}
  \missingfigure{}
  \missingfigure{}
  \caption{Visualizations of the internals of the system.}
\end{figure}

\section{Conclusion}

\begin{itemize}
\item What happened?
\item What next?
\end{itemize}

% \section*{Acknowledgements}

% \textbf{Do not} include acknowledgements in the initial version of
% the paper submitted for blind review.

% If a paper is accepted, the final camera-ready version can (and
% probably should) include acknowledgements. In this case, please
% place such acknowledgements in an unnumbered section at the
% end of the paper. Typically, this will include thanks to reviewers
% who gave useful comments, to colleagues who contributed to the ideas,
% and to funding agencies and corporate sponsors that provided financial
% support.

\bibliography{example}
\bibliographystyle{icml2017}

\end{document}

### 2019-05-11 paper/paper.tex
Fix duplicate figure label warning in paper.tex
Setting up notation

@@
 \usepackage{macros}
+
+\newcommand{\bert}{\operatorname{BERT}}
+\newcommand{\distortion}{\operatorname{Distortion}}
+\newcommand{\prune}{\operatorname{Prune}}
+\newcommand{\diffprune}{\operatorname{DiffPrune}}
+
+\newcommand{\btheta}{{\bm{\theta}}}
+\newcommand{\bphi}{{\bm{\phi}}}
+\newcommand{\bpsi}{{\bm{\psi}}}
 
@@
 
+We first set up some notation. Let $F_\btheta = G_\bpsi \circ \bert_\bphi$ be a
+transformed model where
+$\btheta = (\bphi, \bpsi)$ be parameters of the subparts of the model.
+$\bert_\bphi$ is a BERT model where the pretrained weights are $\bphi_0 = 
+(\bphi_0^i)_{i=1}^n$, and
+$G_\bpsi$ is additional layers for fine-tuning BERT, parameterized by $\bpsi$.
+We decompose the subparts of the model into layers: \begin{align*}
+\bert_\bphi &= f_{n}^{\bphi_n} \circ \cdots \circ f_1^{\bphi_1} \\
+G_\bpsi &= g_{m}^{\bpsi_m} \circ \cdots \circ g_1^{\bpsi_1}.
+\end{align*}
+
+\subsection{DeepTwist-based Weight Distortions}
+
 Example Structure:
@@
 
+\begin{comment}
 \begin{itemize}
@@
 \end{itemize}
+\end{comment}
 
@@
 
-\begin{table}
-  \centering
-  \missingfigure[figheight=5cm]{}
-  \caption{Secondary table or figure in results section.}
-  \label{fig:mainres}
-\end{table}
+% \begin{table}
+%   \centering
+%   \missingfigure[figheight=5cm]{}
+%   \caption{Secondary table or figure in results section.}
+%   \label{fig:mainres}
+% \end{table}
 

### 2019-05-11 paper/paper.tex
Add background in paper

--- 2019-05-10 paper/paper.tex
@@
 \section{Background}
-Example Structure:
-\begin{itemize}
-\item What information does a non-expert need to know about the problem domain?
-\item What data exists for this problem?
-\item What are the challenges/opportunities inherent to the data? (High dimensional, sparse, missing data, noise, structure, discrete/continuous, etc?)
-\end{itemize}
+Deep Neurel Networks (DNNs) have become extremely large in size with growing complexities.
+A BERT base model has 110M parameters and takes 438 MB disk space to store.
+This makes it very hard to deploy those models on mobile devices, which in most cases have limited storage and RAM and lower computational resources.
+The challenge that we are facing is how to compress DNNs in size while keeping their predictive performance competitive with full model.
+
+% Example Structure:
+% \begin{itemize}
+% \item What information does a non-expert need to know about the problem domain?
+% \item What data exists for this problem?
+% \item What are the challenges/opportunities inherent to the data? (High dimensional, sparse, missing data, noise, structure, discrete/continuous, etc?)
+% \end{itemize}
 

### 2019-05-11 paper/paper.tex
Add bibliography
First paragraph on KD

@@
 \section{Background}
-Deep Neurel Networks (DNNs) have become extremely large in size with growing complexities.
-A BERT base model has 110M parameters and takes 438 MB disk space to store.
-This makes it very hard to deploy those models on mobile devices, which in most cases have limited storage and RAM and lower computational resources.
-The challenge that we are facing is how to compress DNNs in size while keeping their predictive performance competitive with full model.
 
@@
 
+Deep Neurel Networks (DNNs) have become extremely large in size with growing complexities.
+A BERT base model has 110M parameters and takes 438 MB disk space to store.
+This makes it very hard to deploy those models on mobile devices, which in most cases have limited storage and RAM and lower computational resources.
+The challenge that we are facing is how to compress DNNs in size while keeping their predictive performance competitive with full model.
+
 \section{Related Work}
 
-Example Structure:
-\begin{itemize}
-\item What 3-5 papers have been published in this space?
-\item How do these  differ from your approach?
-\item What data or methodologies do each of these works use?
-\item How do you plan to compare to these methods?
-\end{itemize}
+% Example Structure:
+% \begin{itemize}
+% \item What 3-5 papers have been published in this space?
+% \item How do these  differ from your approach?
+% \item What data or methodologies do each of these works use?
+% \item How do you plan to compare to these methods?
+% \end{itemize}
+
+We are interested in compressing the language representation model BERT \cite{devlin2018bert}.
+It is the state-of-art result in many natural language processing tasks such as natural language inference, paraphrasing and named entity recognition.
+
+\cite{cheng2017survey} provides a comprehensive overview of the state-of-art methods to compress DNNs.
+Of the methods summarized by the paper, the ones that are of interest to our work are weight-pruning and quantization \cite{han2015deep}, and low-rank factorization \cite{denton2014exploiting}.
+Knowledge distillation, first proposed by \cite{bucilua2006model} as ``knowledge transfer'', was recently popularized by \cite{hinton2015distilling}.
+It differs from the previously mentioned methods since it compresses an existing model by replacing it with a simpler model that is trained on its outputs.
+
+DeepTwist, a end-to-end training framework, allows us to incorporate compression procedures into training \cite{lee2018deeptwist}.
+Under this framework, the model parameters are occasionally distorted during training time instead of only at the end.
+This framework has the benefit of simplified training procedure and faster convergence and reduced requirement for hyperparameter tuning.
+Experiment on MNIST dataset with DeepTwist shows that LeNet-5 and LeNet-300-100 models are able to retain predictive accuracy under high compression rate.
 
@@
 \section{Inference (or Training)}
+\label{sec:training}
+
+\subsection{Knowledge Distillation}
+\label{subsec:kd}
+
+In this paper, we limit our purview to text classification tasks. Training
+neural-network-based systems for this task typically consists of a form of
+gradient descent based on a differentiable loss function which takes in the
+prediction for a given example and the correct label. That is, if we have
+training data $(\bm{x}_i, y_i)$ and model $f$, we would aim to minimize,
+\[ \ell(f(\bm{x_i}), y_i)\]
+where usually the loss function is taken to be Cross-Entropy loss. When we
+already have a model $f$ that performs well, we can leverage this training
+paradigm through a modification called \emph{knowledge distillation}. Given the
+large model that performs well, termed the \emph{teacher network}, we train a
+smaller network $g$, the \emph{student network}, by minimizing,
+\[ \ell(g(\bm{x_i}), f(\bm{x_i})).\]
+Here, we can no longer use Cross-Entropy loss because $f(\bm{x}_i)$ is a
+probability distribution rather than a specific label. However, we can take
+$\ell$ to be either mean-square error (MSE) between the probabilities in
+log-space, or Kullback-Leibler (KL) loss. We avoid MSE error on the
+probabilities themselves because of disappearing gradients when the predicted
+probabilities are very close to 0 or 1.
+
+% TODO: talk about KD
+
+\subsection{Deep Twist}
+
+% TODO: talk about DeepTwist™
 
@@
 
-\bibliography{example}
+\bibliography{paper}
 \bibliographystyle{icml2017}

### 2019-05-11 paper/paper.tex
Add related work

@@
 \section{Inference (or Training)}
-\label{sec:training}
-
-\subsection{Knowledge Distillation}
-\label{subsec:kd}
-
-In this paper, we limit our purview to text classification tasks. Training
-neural-network-based systems for this task typically consists of a form of
-gradient descent based on a differentiable loss function which takes in the
-prediction for a given example and the correct label. That is, if we have
-training data $(\bm{x}_i, y_i)$ and model $f$, we would aim to minimize,
-\[ \ell(f(\bm{x_i}), y_i)\]
-where usually the loss function is taken to be Cross-Entropy loss. When we
-already have a model $f$ that performs well, we can leverage this training
-paradigm through a modification called \emph{knowledge distillation}. Given the
-large model that performs well, termed the \emph{teacher network}, we train a
-smaller network $g$, the \emph{student network}, by minimizing,
-\[ \ell(g(\bm{x_i}), f(\bm{x_i})).\]
-Here, we can no longer use Cross-Entropy loss because $f(\bm{x}_i)$ is a
-probability distribution rather than a specific label. However, we can take
-$\ell$ to be either mean-square error (MSE) between the probabilities in
-log-space, or Kullback-Leibler (KL) loss. We avoid MSE error on the
-probabilities themselves because of disappearing gradients when the predicted
-probabilities are very close to 0 or 1.
-
-% TODO: talk about KD
-
-\subsection{Deep Twist}
-
-% TODO: talk about DeepTwist™
 

### 2019-05-11 paper/paper.tex
Add more to KD section

--- 2019-05-11 paper/paper.tex
@@
 \section{Model}
+\label{sec:model}
 
@@
 probabilities are very close to 0 or 1.
+
+The benefits of training in this fashion have been empirically documented
+% TODO: paper on KD doing well?
+and have theoretical motivation. Our goal of any network is to learn the
+conditional distribution 
+\[ p(y_i = k \mid \bm{x}_i).\]
+In traditional training, we do this by observing the draws $y_i$ from this
+distribution. However, to the extent that the teacher network prediction is a
+good approximation of the true conditional distribution, the student network can
+learn faster because it is being pushed toward predicting the de-noised
+expectation.
+
+To present a simplified example: if a neural network were trying to understand a
+coin flip, it would require a number of observations of heads and tails to
+conclude the underlying probability is 50\% toward either direction. However, if
+it is directly shown that the probability was 50\% each time, regardless of what
+the coin came up, it will in less time understand that the probability is always
+50\%.
+
+An additional benefit from knowledge distillation arises from BERT's
+pre-training. Because BERT is pre-trained on large amounts of unstructured data,
+it contains a powerful language model which likely would be impossible to learn
+from the specific task's data-set. To an extent, relevant features from this
+language model are what make BERT so powerful once it's fine-tuned. Training the
+student network on BERT's output thus allows some of this ``outside knowledge''
+to percolate toward the student network.
+
+To provide a concrete example of how this might work, suppose BERT captures from
+its pre-training that ``bad'', ``horrible,'' and ``terrible'' are approximate
+synonyms. In a sentiment task, these three words appear in three different
+sentences, two of which are negative, and one of which is positive. A fine-tuned
+BERT may provide a lower likelihood of being positive to the positive sentence
+than it would otherwise even if
+
+% TODO: KD benefits
+
+For our knowledge distillation, we make use of a fine-tuned BERT on a task as
+our teacher network and train a simpler model to emulate the predictions use
+\nameref{sec:model}
 

### 2019-05-11 paper/paper.tex
Adding model section and resolving conflicts

@@
 \newcommand{\diffprune}{\operatorname{DiffPrune}}
+\newcommand{\rankreduce}{\operatorname{RankReduce}}
 
@@
 \newcommand{\bpsi}{{\bm{\psi}}}
+\newcommand{\bvartheta}{{\bm{\vartheta}}}
 
@@
 \subsection{DeepTwist-based Weight Distortions}
+
+Given training data $(\bm x_i, y_i)_{i=1}^N$, where $\bm x_i$ are one-hot
+encoded tokens, we train by solving the standard maximum likelihood problem
+where \[
+\min_{\btheta} \sum_{i=1}^N L\pr{y_i, F_\btheta(\bm x_i)}
+\]
+for some loss function specific to the task. For instance, $L$ is cross-entropy
+loss for a (multiclass) classification problem, and $L$ is mean-squared-error
+for a regression problem, which correspond to log-likelihoods in Categorical and
+Gaussian models, respectively. The innovation of DeepTwist-based training is
+perturbing the usual gradient-based optimization by repeatedly distorting the
+current weights to achieve compression objectives.
+
+Specifically, the DeepTwist framework presented in \Cref{sec:training} applies a
+distortion
+step for fixed intervals during training, where \[
+\btheta \gets \distortion(\btheta). 
+\]
+In this section, we discuss a few methods for parameterizing $\distortion$.
+Generally, we may imagine a few special cases of distortion, we call a
+particular distortion \emph{distortion by layer} if it is applied per layer,
+i.e. \begin{align*}
+\distortion'(\btheta) = (&\distortion(\bphi_1),\ldots,\distortion(\bphi_n),\\
+&\distortion(\bpsi_1),\ldots, \distortion(\bpsi_m)).
+\end{align*}
+We call a particular distortion \emph{pretrained-only} if \[
+\distortion'(\btheta) = \distortion(\bphi).
+\]
+
+We list a few methods of parameterizing the distortion step. 
+\paragraphdot{Pruning} Consider a parameter vector $\bvartheta$, let
+  $t_p$ be the $p$-th quantile of the vector $\bvartheta$. Then \[
+  \prune(\bvartheta; p) = \one(|\bvartheta| > t_p) \odot \bvartheta
+  \]
+  be the vector where values in $\bvartheta$ below $t_p$ are zeroed.
+
+  Pruning is an extremely simple procedure. When $p$ is large, say, $p=0.99$, we
+  may take advantage of sparsity of the resulting model by saving locations of
+  nonzero entries, and thus reducing the model size in memory. However, such
+  compression does not come without potential sacrifices to computational speed,
+  as computation needed to be carried out on sparse data structures, which may
+  not effectively make use of standard hardware.
+
+  Pruning is an out-of-the-box procedure that works with any models. However, as
+  a price of the generality, pruning fails to be tailored to the nature of BERT
+  being a pre-trained model. Suppose the pretrained weights $\bphi_0 $ capture
+  certain structure of language, then dramatic distortions to $\bphi_0$
+  essentially discards the information, especially early in the training loop.
+  We may partially remedy this issue by either using a dynamic pruning rate,
+  where pruning rate is small early in the training loop or by using
+  layer-specific pruning rates, with layers in $\bert$ having a lower pruning
+  rate than layers in $G$.
+
+  A direct approach to taking advantage of pretrained models, however, is 
+  \emph{difference pruning}, where we ensure that
+  the difference between the model and a pretrained model is sparse.
+  Effectively, difference pruning ensures a form of weight sharing between
+  various BERT-based models for different tasks.
+
+\paragraphdot{Difference Pruning} Consider some pretrained weights
+$\bvartheta_0$, define \[
+\diffprune(\bvartheta; \bvartheta_0, p ) = \bvartheta_0 + \prune(\bvartheta -
+\bvartheta_0 ; p). 
+\]
+Observe that difference pruning provides no compression benefits when there is
+only one fine-tuning task; however, when the number of potential tasks is large,
+we only need to save $\btheta_0$ and the sparse matrix $\btheta - \btheta_0,$
+and $\btheta_0$ is shared across tasks.
+
+Observe that we can transform any reduction technique by applying the reduction
+technique on the difference, and thus the \emph{difference} should be viewed 
+(and is implemented) as a decorator to a conventional distortion technique.
+
+\paragraph{Rank Reduction} If $\bvartheta$ is a matrix, then we may apply rank
+reduction via singular value decomposition \[
+\bvartheta = U\Sigma V^\top
+\]
+where $\Sigma$ is a diagonal matrix, where $U \in $
+
+We distort via \[
+\rankreduce(\bvartheta) = \tilde U \tilde \Sigma \tilde V^\top,
+\]
+where $\tilde U, \tilde \Sigma, \tilde V$ are conforming matrices such that the
+smallest values on the spectrum $\Sigma$ is zeroed out, as well as corresponding
+values in $U,V$. If we keep only the $r$ largest spectral values, then we store
+$\tilde U, \tilde \Sigma$, an $n\times r$ matrix
 

### 2019-05-11 paper/paper.tex
Fix citation style

@@
 
-We are interested in compressing the language representation model BERT \cite{devlin2018bert}.
+We are interested in compressing the language representation model BERT \citep{devlin2018bert}.
 It is the state-of-art result in many natural language processing tasks such as natural language inference, paraphrasing and named entity recognition.
 
-\cite{cheng2017survey} provides a comprehensive overview of the state-of-art methods to compress DNNs.
-Of the methods summarized by the paper, the ones that are of interest to our work are weight-pruning and quantization \cite{han2015deep}, and low-rank factorization \cite{denton2014exploiting}.
-Knowledge distillation, first proposed by \cite{bucilua2006model} as ``knowledge transfer'', was recently popularized by \cite{hinton2015distilling}.
+\citet{cheng2017survey} provides a comprehensive overview of the state-of-art methods to compress DNNs.
+Of the methods summarized by the paper, the ones that are of interest to our work are weight-pruning and quantization \citep{han2015deep}, and low-rank factorization \citep{denton2014exploiting}.
+Knowledge distillation, first proposed by \citet{bucilua2006model} as ``knowledge transfer'', was recently popularized by \citet{hinton2015distilling}.
 It differs from the previously mentioned methods since it compresses an existing model by replacing it with a simpler model that is trained on its outputs.
 
-DeepTwist, a end-to-end training framework, allows us to incorporate compression procedures into training \cite{lee2018deeptwist}.
+DeepTwist, a end-to-end training framework, allows us to incorporate compression procedures into training \citep{lee2018deeptwist}.
 Under this framework, the model parameters are occasionally distorted during training time instead of only at the end.

### 2019-05-11 paper/paper.tex
Resolving merge conflicts, SVD

--- 2019-05-11 paper/paper.tex
@@
-\documentclass{article}
+\documentclass[11pt]{article}
 
@@
 
-We are interested in compressing the language representation model BERT \cite{devlin2018bert}.
-It is the state-of-art result in many natural language processing tasks such as natural language inference, paraphrasing and named entity recognition.
+We are interested in compressing the language representation model BERT \citep{devlin2018bert}. 
+It is the state-of-art result in many natural language processing tasks 
+such as natural language inference, paraphrasing and named entity recognition.
 
-\cite{cheng2017survey} provides a comprehensive overview of the state-of-art methods to compress DNNs.
+\citet{cheng2017survey} provides a comprehensive overview of the state-of-art methods to compress DNNs.
 Of the methods summarized by the paper, the ones that are of interest to our work are weight-pruning and quantization \cite{han2015deep}, and low-rank factorization \cite{denton2014exploiting}.
@@
 
-DeepTwist, a end-to-end training framework, allows us to incorporate compression procedures into training \cite{lee2018deeptwist}.
+DeepTwist, a end-to-end training framework, allows us to incorporate compression procedures into training \citep{lee2018deeptwist}.
 Under this framework, the model parameters are occasionally distorted during training time instead of only at the end.
@@
 
-\subsection{DeepTwist-based Weight Distortions}
+% \subsection{DeepTwist-based Weight Distortions}
 
@@
 where \[
-\min_{\btheta} \sum_{i=1}^N L\pr{y_i, F_\btheta(\bm x_i)}
+\min_{\btheta} \sum_{i=1}^N \ell\pr{y_i, F_\btheta(\bm x_i)}
 \]
-for some loss function specific to the task. For instance, $L$ is cross-entropy
-loss for a (multiclass) classification problem, and $L$ is mean-squared-error
+for some loss function specific to the task. For instance, $\ell$ is cross-entropy
+loss for a (multiclass) classification problem, and $\ell$ is mean-squared-error
 for a regression problem, which correspond to log-likelihoods in Categorical and
@@
 i.e. \begin{align*}
-\distortion'(\btheta) = (&\distortion(\bphi_1),\ldots,\distortion(\bphi_n),\\
+\distortion'(\btheta) &= \\ (&\distortion(\bphi_1),\ldots,\distortion(\bphi_n),\\
 &\distortion(\bpsi_1),\ldots, \distortion(\bpsi_m)).
@@
 
-\paragraph{Rank Reduction} If $\bvartheta$ is a matrix, then we may apply rank
+\paragraphdot{Rank Reduction} If $\bvartheta$ is a matrix, then we may apply
+rank
 reduction via singular value decomposition \[
@@
 \]
-where $\Sigma$ is a diagonal matrix, where $U \in $
+where $\Sigma$ is a diagonal matrix, where $U \in \R^{n\times n}, \Sigma\in \R^
+{n\times n}, V\in \R^{m\times n}$, and $\bvartheta \in \R^{n\times m}$.
 
@@
 values in $U,V$. If we keep only the $r$ largest spectral values, then we store
-$\tilde U, \tilde \Sigma$, an $n\times r$ matrix
+$\tilde U \tilde \Sigma$, an $n\times r$ matrix, and $\tilde V$, an $m\times r$
+matrix. Thus, instead of storing $2nm$ floats, we may store $r(n+m)$, achieving
+a compression rate of \[
+\rho = \frac{r(n+m)}{2mn}.
+\]
+Note however, that storing matrices in this manner requires an additional
+matrix multiplication in evaluation time, since we have to compute the product
+$\tilde U \tilde \Sigma \tilde V$.
 
-Example Structure:
+% \subsection{Knowledge Distillation}
 
-\begin{itemize}
-\item What is the formal definition of your problem?
-\item What is the precise mathematical model you are using to represent it? In almost all cases this will use the probabilistic language from class, e.g.
-  \begin{equation}
-  z \sim {\cal N}(0, \sigma^2)\label{eq:1}
-\end{equation}
-But it may also be a neural network, or a non-probabilistic loss,
-\[ h_t \gets \mathrm{RNN}(x_{t}, h_{t-1} )\]
+% Example Structure:
 
-This is also a good place to reference a diagram such as Figure~\ref{fig:diagram}.
+% \begin{itemize}
+% \item What is the formal definition of your problem?
+% \item What is the precise mathematical model you are using to represent it? In almost all cases this will use the probabilistic language from class, e.g.
+%   \begin{equation}
+%   z \sim {\cal N}(0, \sigma^2)\label{eq:1}
+% \end{equation}
+% But it may also be a neural network, or a non-probabilistic loss,
+% \[ h_t \gets \mathrm{RNN}(x_{t}, h_{t-1} )\]
 
-\item What are the parameters or latent variables of this model that you plan on estimating or inferring?
+% This is also a good place to reference a diagram such as Figure~\ref{fig:diagram}.
+
+% \item What are the parameters or latent variables of this model that you plan on estimating or inferring?
 Be explicit.
@@
 How do these relate to the original problem description?
-\end{itemize}
+% \end{itemize}
 
@@
 % TODO: paper on KD doing well? 
+\citep{hinton2015distilling}
 and have theoretical motivation. Our goal of any network is to learn the

### 2019-05-11 paper/paper.tex
Model and experimental setup

@@
 We distort via \[
-\rankreduce(\bvartheta) = \tilde U \tilde \Sigma \tilde V^\top,
+\rankreduce(\bvartheta; r) = \tilde U \tilde \Sigma \tilde V^\top,
 \]
@@
 \section{Methods}
+In this section, we briefly discuss our experimental setup. We mostly
+work with
+SST-2, a binary sentiment classification task in the GLUE multitask benchmark
+framework \citep{wang2018glue}. We also validate the model's
+performance with trial on the Quora Question Pair (QQP) task, which is a
+binary classification task for whether two questions are equivalent. We
+train with a maximum sequence length of 64 and batch size of 32 on the
+NC-6 and NC-12 virtual machines on Microsoft Azure. We use the basic 
+\texttt{BERT-base-uncased} model for our experimental results. We employ
+early stopping in training, with patience of 1 epoch, and early stopping is
+guided by validation error.
 
-\begin{itemize}
-\item What are the exact details of the dataset that you used? (Number of data points / standard or non-standard / synthetic or real / exact form of the data)
+\subsection{DeepTwist}
+We implement the DeepTwist framework with default frequency of distortion
+every 10 batches. Additionally, we ensure that training ends on a
+distortion step, so that the model produced by training has compression
+benefits. For $\prune$ and $\diffprune$ distortions, we use a single
+pruning rate held fixed throughout training.
 
-\item What are the exact details of the features you computed?
+\subsection{Knowledge Distillation}
+For knowledge distillation experiments, we use various configurations of
+the student network:
+\paragraphdot{LSTM} We use a one-layer LSTM network with hidden dimension
+$H=200$. We first embed the one-hot representation of tokens, and we feed
+the embeddings through an LSTM. We then map the last hidden state of the
+LSTM through a linear layer for classification. 
+\paragraphdot{CNN} We use an implementation\footnote{\url{https://github.com/jfilter/cnn-text-classification-pytorch/blob/master/cnn_text_classification/model.py}} 
+of \citet{kim2014convolutional} with kernel sizes $(3,4,5)$, hidden size
+$H=300$, no dropout, and $20$ kernels for each kernel size.\footnote{These
+are default in the implementation we used.}
 
-\item How did you train or run inference? (Optimization method / hyperparameter settings / amount of time ran / what did you implement versus borrow / how were baselines computed).
-
-\item What are the exact details of the metric used?
-\end{itemize}
+For each model, we initialize the embedding layer of the model with the
+first $H$ dimensions of the corresponding embedding layer in pretrained
+BERT.
 

### 2019-05-11 paper/paper.tex
Move training section before model section
Comment out default figures

@@
 Experiment on MNIST dataset with DeepTwist shows that LeNet-5 and LeNet-300-100 models are able to retain predictive accuracy under high compression rate.
+
+\section{Inference (or Training)}
+\label{sec:training}
+
+\subsection{Knowledge Distillation}
+\label{subsec:kd}
+
+In this paper, we limit our purview to text classification tasks. Training
+neural-network-based systems for this task typically consists of a form of
+gradient descent based on a differentiable loss function which takes in the
+prediction for a given example and the correct label. That is, if we have
+training data $(\bm{x}_i, y_i)$ and model $f$, we would aim to minimize,
+\[ \ell(f(\bm{x_i}), y_i)\]
+where usually the loss function is taken to be Cross-Entropy loss. When we
+already have a model $f$ that performs well, we can leverage this training
+paradigm through a modification called \emph{knowledge distillation}. Given the
+large model that performs well, termed the \emph{teacher network}, we train a
+smaller network $g$, the \emph{student network}, by minimizing,
+\[ \ell(g(\bm{x_i}), f(\bm{x_i})).\]
+Here, we can no longer use Cross-Entropy loss because $f(\bm{x}_i)$ is a
+probability distribution rather than a specific label. However, we can take
+$\ell$ to be either mean-square error (MSE) between the probabilities in
+log-space, or Kullback-Leibler (KL) loss. We avoid MSE error on the
+probabilities themselves because of disappearing gradients when the predicted
+probabilities are very close to 0 or 1.
+
+The benefits of training in this fashion have been empirically documented
+% TODO: paper on KD doing well? 
+\citep{hinton2015distilling}
+and have theoretical motivation. Our goal of any network is to learn the
+conditional distribution 
+\[ p(y_i = k \mid \bm{x}_i).\]
+In traditional training, we do this by observing the draws $y_i$ from this
+distribution. However, to the extent that the teacher network prediction is a
+good approximation of the true conditional distribution, the student network can
+learn faster because it is being pushed toward predicting the de-noised
+expectation.
+
+To present a simplified example: if a neural network were trying to understand a
+coin flip, it would require a number of observations of heads and tails to
+conclude the underlying probability is 50\% toward either direction. However, if
+it is directly shown that the probability was 50\% each time, regardless of what
+the coin came up, it will in less time understand that the probability is always
+50\%.
+
+An additional benefit from knowledge distillation arises from BERT's
+pre-training. Because BERT is pre-trained on large amounts of unstructured data,
+it contains a powerful language model which likely would be impossible to learn
+from the specific task's data-set. To an extent, relevant features from this
+language model are what make BERT so powerful once it's fine-tuned. Training the
+student network on BERT's output thus allows some of this ``outside knowledge''
+to percolate toward the student network.
+
+To provide a concrete example of how this might work, suppose BERT captures from
+its pre-training that ``bad'', ``horrible,'' and ``terrible'' are approximate
+synonyms. In a sentiment task, these three words appear in three different
+sentences, two of which are negative, and one of which is positive. A fine-tuned
+BERT may provide a lower likelihood of being positive to the positive sentence
+than it would otherwise even if
+
+% TODO: KD benefits
+
+For our knowledge distillation, we make use of a fine-tuned BERT on a task as
+our teacher network and train a simpler model to emulate the predictions use
+\nameref{sec:model}
+
+% TODO: talk about KD
+
+\subsection{Deep Twist}
+
+% TODO: talk about DeepTwist™
+
+\begin{comment}
+\begin{itemize}
+\item How do you plan on training your parameters / inferring the
+  states of your latent variables (MLE / MAP / Backprop / VI / EM / BP / ...)
+
+\item What are the assumptions implicit in this technique? Is it an approximation or exact? If it is an approximation what bound does it optimize?
+
+\item What is the explicit method / algorithm that you derive for learning these parameters?
+\end{itemize}
+\end{comment}
+
+\begin{algorithm}
+  \begin{algorithmic}
+    \STATE{}
+  \end{algorithmic}
+  \caption{Your Pseudocode}
+\end{algorithm}
 
@@
 
-\begin{figure}
-  \centering
-  \missingfigure[figheight=8cm]{}
-  \caption{\label{fig:diagram} This is a good place to include a diagram showing how your model works. Examples include a graphical model or a neural network block diagram.}
-\end{figure}
-
-\section{Inference (or Training)}
-\label{sec:training}
-
-\subsection{Knowledge Distillation}
-\label{subsec:kd}
-
-In this paper, we limit our purview to text classification tasks. Training
-neural-network-based systems for this task typically consists of a form of
-gradient descent based on a differentiable loss function which takes in the
-prediction for a given example and the correct label. That is, if we have
-training data $(\bm{x}_i, y_i)$ and model $f$, we would aim to minimize,
-\[ \ell(f(\bm{x_i}), y_i)\]
-where usually the loss function is taken to be Cross-Entropy loss. When we
-already have a model $f$ that performs well, we can leverage this training
-paradigm through a modification called \emph{knowledge distillation}. Given the
-large model that performs well, termed the \emph{teacher network}, we train a
-smaller network $g$, the \emph{student network}, by minimizing,
-\[ \ell(g(\bm{x_i}), f(\bm{x_i})).\]
-Here, we can no longer use Cross-Entropy loss because $f(\bm{x}_i)$ is a
-probability distribution rather than a specific label. However, we can take
-$\ell$ to be either mean-square error (MSE) between the probabilities in
-log-space, or Kullback-Leibler (KL) loss. We avoid MSE error on the
-probabilities themselves because of disappearing gradients when the predicted
-probabilities are very close to 0 or 1.
-
-The benefits of training in this fashion have been empirically documented
-% TODO: paper on KD doing well? 
-\citep{hinton2015distilling}
-and have theoretical motivation. Our goal of any network is to learn the
-conditional distribution 
-\[ p(y_i = k \mid \bm{x}_i).\]
-In traditional training, we do this by observing the draws $y_i$ from this
-distribution. However, to the extent that the teacher network prediction is a
-good approximation of the true conditional distribution, the student network can
-learn faster because it is being pushed toward predicting the de-noised
-expectation.
-
-To present a simplified example: if a neural network were trying to understand a
-coin flip, it would require a number of observations of heads and tails to
-conclude the underlying probability is 50\% toward either direction. However, if
-it is directly shown that the probability was 50\% each time, regardless of what
-the coin came up, it will in less time understand that the probability is always
-50\%.
-
-An additional benefit from knowledge distillation arises from BERT's
-pre-training. Because BERT is pre-trained on large amounts of unstructured data,
-it contains a powerful language model which likely would be impossible to learn
-from the specific task's data-set. To an extent, relevant features from this
-language model are what make BERT so powerful once it's fine-tuned. Training the
-student network on BERT's output thus allows some of this ``outside knowledge''
-to percolate toward the student network.
-
-To provide a concrete example of how this might work, suppose BERT captures from
-its pre-training that ``bad'', ``horrible,'' and ``terrible'' are approximate
-synonyms. In a sentiment task, these three words appear in three different
-sentences, two of which are negative, and one of which is positive. A fine-tuned
-BERT may provide a lower likelihood of being positive to the positive sentence
-than it would otherwise even if
-
-% TODO: KD benefits
-
-For our knowledge distillation, we make use of a fine-tuned BERT on a task as
-our teacher network and train a simpler model to emulate the predictions use
-\nameref{sec:model}
-
-% TODO: talk about KD
-
-\subsection{Deep Twist}
-
-% TODO: talk about DeepTwist™
-
-\begin{comment}
-\begin{itemize}
-\item How do you plan on training your parameters / inferring the
-  states of your latent variables (MLE / MAP / Backprop / VI / EM / BP / ...)
-
-\item What are the assumptions implicit in this technique? Is it an approximation or exact? If it is an approximation what bound does it optimize?
-
-\item What is the explicit method / algorithm that you derive for learning these parameters?
-\end{itemize}
-\end{comment}
-
-\begin{algorithm}
-  \begin{algorithmic}
-    \STATE{}
-  \end{algorithmic}
-  \caption{Your Pseudocode}
-\end{algorithm}
+% \begin{figure}
+%   \centering
+%   \missingfigure[figheight=8cm]{}
+%   \caption{\label{fig:diagram} This is a good place to include a diagram showing how your model works. Examples include a graphical model or a neural network block diagram.}
+% \end{figure}
 
@@
 
-\begin{table*}
-  \centering
-  \missingfigure{}
-  \caption{This is usually a table. Tables with numbers are generally easier to read than graphs, so prefer when possible.}
-  \label{fig:mainres}
-\end{table*}
+% \begin{table*}
+%   \centering
+%   \missingfigure{}
+%   \caption{This is usually a table. Tables with numbers are generally easier to read than graphs, so prefer when possible.}
+%   \label{fig:mainres}
+% \end{table*}
 
@@
 
-\begin{figure}
-  \centering
-  \missingfigure{}
-  \missingfigure{}
-  \missingfigure{}
-  \caption{Visualizations of the internals of the system.}
-\end{figure}
+% \begin{figure}
+%   \centering
+%   \missingfigure{}
+%   \missingfigure{}
+%   \missingfigure{}
+%   \caption{Visualizations of the internals of the system.}
+% \end{figure}
 

### 2019-05-11 paper/paper.tex
Modify background

--- 2019-05-11 paper/paper.tex
@@
 
-Deep Neurel Networks (DNNs) have become extremely large in size with growing complexities.
-A BERT base model has 110M parameters and takes 438 MB disk space to store.
-This makes it very hard to deploy those models on mobile devices, which in most cases have limited storage and RAM and lower computational resources.
-The challenge that we are facing is how to compress DNNs in size while keeping their predictive performance competitive with full model.
+Deep Neurel Networks (DNNs) have become extremely large in size with growing
+complexities. A BERT base model has 110M parameters and takes 438 MB disk space
+to store. This makes it very hard to deploy those models on mobile devices,
+which in most cases have limited storage and RAM and lower computational
+resources. As a result, we are not able to store multiple models for different
+tasks on mobile devices, and evaluating one single model also takes too much
+time due to computational capacity limit. The challenge that we are facing is
+how to compress DNNs in size while keeping their predictive performance
+competitive with full model.
 
@@
 
-We are interested in compressing the language representation model BERT \citep{devlin2018bert}. 
-It is the state-of-art result in many natural language processing tasks 
-such as natural language inference, paraphrasing and named entity recognition.
+We are interested in compressing the language representation model BERT
+\citep{devlin2018bert}.  It is the state-of-art result in many natural language
+processing tasks  such as natural language inference, paraphrasing and named
+entity recognition.
 
-\citet{cheng2017survey} provides a comprehensive overview of the state-of-art methods to compress DNNs.
-Of the methods summarized by the paper, the ones that are of interest to our work are weight-pruning and quantization \cite{han2015deep}, and low-rank factorization \cite{denton2014exploiting}.
-Knowledge distillation, first proposed by \cite{bucilua2006model} as ``knowledge transfer'', was recently popularized by \cite{hinton2015distilling}.
-It differs from the previously mentioned methods since it compresses an existing model by replacing it with a simpler model that is trained on its outputs.
+\citet{cheng2017survey} provides a comprehensive overview of the state-of-art
+methods to compress DNNs. Of the methods summarized by the paper, the ones
+that are of interest to our work are weight-pruning and quantization
+\cite{han2015deep}, and low-rank factorization \cite{denton2014exploiting}.
+Knowledge distillation, first proposed by \cite{bucilua2006model} as
+``knowledge transfer'', was recently popularized by
+\cite{hinton2015distilling}. It differs from the previously mentioned methods
+since it compresses an existing model by replacing it with a simpler model
+that is trained on its outputs.
 
-DeepTwist, a end-to-end training framework, allows us to incorporate compression procedures into training \citep{lee2018deeptwist}.
-Under this framework, the model parameters are occasionally distorted during training time instead of only at the end.
-This framework has the benefit of simplified training procedure and faster convergence and reduced requirement for hyperparameter tuning.
-Experiment on MNIST dataset with DeepTwist shows that LeNet-5 and LeNet-300-100 models are able to retain predictive accuracy under high compression rate.
+DeepTwist, a end-to-end training framework, allows us to incorporate compression
+procedures into training \citep{lee2018deeptwist}. Under this framework, the
+model parameters are occasionally distorted during training time instead of only
+at the end. This framework has the benefit of simplified training procedure and
+faster convergence and reduced requirement for hyperparameter tuning. Experiment
+on MNIST dataset with DeepTwist shows that LeNet-5 and LeNet-300-100 models are
+able to retain predictive accuracy under high compression rate.
 

### 2019-05-11 paper/paper.tex
Fix last HEAD

@@
 that are of interest to our work are weight-pruning and quantization
-\cite{han2015deep}, and low-rank factorization \cite{denton2014exploiting}.
-Knowledge distillation, first proposed by \cite{bucilua2006model} as
+\citep{han2015deep}, and low-rank factorization \citep{denton2014exploiting}.
+Knowledge distillation, first proposed by \citep{bucilua2006model} as
 ``knowledge transfer'', was recently popularized by
-\cite{hinton2015distilling}. It differs from the previously mentioned methods
+\citep{hinton2015distilling}. It differs from the previously mentioned methods
 since it compresses an existing model by replacing it with a simpler model
@@
 able to retain predictive accuracy under high compression rate.
+
+\section{Inference (or Training)}
+\label{sec:training}
+
+\subsection{Knowledge Distillation}
+\label{subsec:kd}
+
+In this paper, we limit our purview to text classification tasks. Training
+neural-network-based systems for this task typically consists of a form of
+gradient descent based on a differentiable loss function which takes in the
+prediction for a given example and the correct label. That is, if we have
+training data $(\bm{x}_i, y_i)$ and model $f$, we would aim to minimize,
+\[ \ell(f(\bm{x_i}), y_i)\]
+where usually the loss function is taken to be Cross-Entropy loss. When we
+already have a model $f$ that performs well, we can leverage this training
+paradigm through a modification called \emph{knowledge distillation}. Given the
+large model that performs well, termed the \emph{teacher network}, we train a
+smaller network $g$, the \emph{student network}, by minimizing,
+\[ \ell(g(\bm{x_i}), f(\bm{x_i})).\]
+Here, we can no longer use Cross-Entropy loss because $f(\bm{x}_i)$ is a
+probability distribution rather than a specific label. However, we can take
+$\ell$ to be either mean-square error (MSE) between the probabilities in
+log-space, or Kullback-Leibler (KL) loss. We avoid MSE error on the
+probabilities themselves because of disappearing gradients when the predicted
+probabilities are very close to 0 or 1.
+
+The benefits of training in this fashion have been empirically documented
+% TODO: paper on KD doing well? 
+\citep{hinton2015distilling}
+and have theoretical motivation. Our goal of any network is to learn the
+conditional distribution 
+\[ p(y_i = k \mid \bm{x}_i).\]
+In traditional training, we do this by observing the draws $y_i$ from this
+distribution. However, to the extent that the teacher network prediction is a
+good approximation of the true conditional distribution, the student network can
+learn faster because it is being pushed toward predicting the de-noised
+expectation.
+
+To present a simplified example: if a neural network were trying to understand a
+coin flip, it would require a number of observations of heads and tails to
+conclude the underlying probability is 50\% toward either direction. However, if
+it is directly shown that the probability was 50\% each time, regardless of what
+the coin came up, it will in less time understand that the probability is always
+50\%.
+
+An additional benefit from knowledge distillation arises from BERT's
+pre-training. Because BERT is pre-trained on large amounts of unstructured data,
+it contains a powerful language model which likely would be impossible to learn
+from the specific task's data-set. To an extent, relevant features from this
+language model are what make BERT so powerful once it's fine-tuned. Training the
+student network on BERT's output thus allows some of this ``outside knowledge''
+to percolate toward the student network.
+
+To provide a concrete example of how this might work, suppose BERT captures from
+its pre-training that ``bad'', ``horrible,'' and ``terrible'' are approximate
+synonyms. In a sentiment task, these three words appear in three different
+sentences, two of which are negative, and one of which is positive. A fine-tuned
+BERT may provide a lower likelihood of being positive to the positive sentence
+than it would otherwise even if
+
+% TODO: KD benefits
+
+For our knowledge distillation, we make use of a fine-tuned BERT on a task as
+our teacher network and train a simpler model to emulate the predictions use
+\nameref{sec:model}
+
+% TODO: talk about KD
+
+\subsection{Deep Twist}
+
+% TODO: talk about DeepTwist™
+
+\begin{comment}
+\begin{itemize}
+\item How do you plan on training your parameters / inferring the
+  states of your latent variables (MLE / MAP / Backprop / VI / EM / BP / ...)
+
+\item What are the assumptions implicit in this technique? Is it an approximation or exact? If it is an approximation what bound does it optimize?
+
+\item What is the explicit method / algorithm that you derive for learning these parameters?
+\end{itemize}
+\end{comment}
+
+\begin{algorithm}
+  \begin{algorithmic}
+    \STATE{}
+  \end{algorithmic}
+  \caption{Your Pseudocode}
+\end{algorithm}
 
@@
 
-\section{Inference (or Training)}
-\label{sec:training}
+% \subsection{Knowledge Distillation}
 
-\subsection{Knowledge Distillation}
-\label{subsec:kd}
+% Example Structure:
 
-In this paper, we limit our purview to text classification tasks. Training
-neural-network-based systems for this task typically consists of a form of
-gradient descent based on a differentiable loss function which takes in the
-prediction for a given example and the correct label. That is, if we have
-training data $(\bm{x}_i, y_i)$ and model $f$, we would aim to minimize,
-\[ \ell(f(\bm{x_i}), y_i)\]
-where usually the loss function is taken to be Cross-Entropy loss. When we
-already have a model $f$ that performs well, we can leverage this training
-paradigm through a modification called \emph{knowledge distillation}. Given the
-large model that performs well, termed the \emph{teacher network}, we train a
-smaller network $g$, the \emph{student network}, by minimizing,
-\[ \ell(g(\bm{x_i}), f(\bm{x_i})).\]
-Here, we can no longer use Cross-Entropy loss because $f(\bm{x}_i)$ is a
-probability distribution rather than a specific label. However, we can take
-$\ell$ to be either mean-square error (MSE) between the probabilities in
-log-space, or Kullback-Leibler (KL) loss. We avoid MSE error on the
-probabilities themselves because of disappearing gradients when the predicted
-probabilities are very close to 0 or 1.
+% \begin{itemize}
+% \item What is the formal definition of your problem?
+% \item What is the precise mathematical model you are using to represent it? In almost all cases this will use the probabilistic language from class, e.g.
+%   \begin{equation}
+%   z \sim {\cal N}(0, \sigma^2)\label{eq:1}
+% \end{equation}
+% But it may also be a neural network, or a non-probabilistic loss,
+% \[ h_t \gets \mathrm{RNN}(x_{t}, h_{t-1} )\]
 
-The benefits of training in this fashion have been empirically documented
-% TODO: paper on KD doing well? 
-\citep{hinton2015distilling}
-and have theoretical motivation. Our goal of any network is to learn the
-conditional distribution 
-\[ p(y_i = k \mid \bm{x}_i).\]
-In traditional training, we do this by observing the draws $y_i$ from this
-distribution. However, to the extent that the teacher network prediction is a
-good approximation of the true conditional distribution, the student network can
-learn faster because it is being pushed toward predicting the de-noised
-expectation.
+% This is also a good place to reference a diagram such as Figure~\ref{fig:diagram}.
 
-To present a simplified example: if a neural network were trying to understand a
-coin flip, it would require a number of observations of heads and tails to
-conclude the underlying probability is 50\% toward either direction. However, if
-it is directly shown that the probability was 50\% each time, regardless of what
-the coin came up, it will in less time understand that the probability is always
-50\%.
+% \item What are the parameters or latent variables of this model that you plan on estimating or inferring?
+Be explicit.
+How many are there?
+Which are you assuming are given?
+How do these relate to the original problem description?
+% \end{itemize}
 
-An additional benefit from knowledge distillation arises from BERT's
-pre-training. Because BERT is pre-trained on large amounts of unstructured data,
-it contains a powerful language model which likely would be impossible to learn
-from the specific task's data-set. To an extent, relevant features from this
-language model are what make BERT so powerful once it's fine-tuned. Training the
-student network on BERT's output thus allows some of this ``outside knowledge''
-to percolate toward the student network.
-
-To provide a concrete example of how this might work, suppose BERT captures from
-its pre-training that ``bad'', ``horrible,'' and ``terrible'' are approximate
-synonyms. In a sentiment task, these three words appear in three different
-sentences, two of which are negative, and one of which is positive. A fine-tuned
-BERT may provide a lower likelihood of being positive to the positive sentence
-than it would otherwise even if
-
-% TODO: KD benefits
-
-For our knowledge distillation, we make use of a fine-tuned BERT on a task as
-our teacher network and train a simpler model to emulate the predictions use
-\nameref{sec:model}
-
-% TODO: talk about KD
-
-\subsection{Deep Twist}
-
-% TODO: talk about DeepTwist™
-
-\begin{comment}
-\begin{itemize}
-\item How do you plan on training your parameters / inferring the
-  states of your latent variables (MLE / MAP / Backprop / VI / EM / BP / ...)
-
-\item What are the assumptions implicit in this technique? Is it an approximation or exact? If it is an approximation what bound does it optimize?
-
-\item What is the explicit method / algorithm that you derive for learning these parameters?
-\end{itemize}
-\end{comment}
-
-\begin{algorithm}
-  \begin{algorithmic}
-    \STATE{}
-  \end{algorithmic}
-  \caption{Your Pseudocode}
-\end{algorithm}
+% \begin{figure}
+%   \centering
+%   \missingfigure[figheight=8cm]{}
+%   \caption{\label{fig:diagram} This is a good place to include a diagram showing how your model works. Examples include a graphical model or a neural network block diagram.}
+% \end{figure}
 

### 2019-05-11 paper/paper.tex
Remove last surviving figure
Adding page number

@@
 
-\icmltitlerunning{CS 287 Final Project Template}
+\icmltitlerunning{BERT Model Compression and Weight Sharing}
 
@@
 already have a model $f$ that performs well, we can leverage this training
-paradigm through a modification called \emph{knowledge distillation}. Given the
-large model that performs well, termed the \emph{teacher network}, we train a
-smaller network $g$, the \emph{student network}, by minimizing,
+paradigm through a modification called \emph{knowledge distillation}. Given
+the large model that performs well, termed the \emph{teacher network}, we
+train a smaller network $g$, the \emph{student network}, by minimizing,
 \[ \ell(g(\bm{x_i}), f(\bm{x_i})).\]
@@
 distribution. However, to the extent that the teacher network prediction is a
-good approximation of the true conditional distribution, the student network can
-learn faster because it is being pushed toward predicting the de-noised
+good approximation of the true conditional distribution, the student network
+can learn faster because it is being pushed toward predicting the de-noised
 expectation.
 
-To present a simplified example: if a neural network were trying to understand a
-coin flip, it would require a number of observations of heads and tails to
-conclude the underlying probability is 50\% toward either direction. However, if
-it is directly shown that the probability was 50\% each time, regardless of what
-the coin came up, it will in less time understand that the probability is always
-50\%.
+To present a simplified example: if a neural network were trying to understand
+a coin flip, it would require a number of observations of heads and tails to
+conclude the underlying probability is 50\% toward either direction. However,
+if it is directly shown that the probability was 50\% each time, regardless of
+what the coin came up, it will in less time understand that the probability is
+always 50\%.
 
 An additional benefit from knowledge distillation arises from BERT's
-pre-training. Because BERT is pre-trained on large amounts of unstructured data,
-it contains a powerful language model which likely would be impossible to learn
-from the specific task's data-set. To an extent, relevant features from this
-language model are what make BERT so powerful once it's fine-tuned. Training the
-student network on BERT's output thus allows some of this ``outside knowledge''
-to percolate toward the student network.
+pre-training. Because BERT is pre-trained on large amounts of unstructured
+data, it contains a powerful language model which likely would be impossible
+to learn from the specific task's data-set. To an extent, relevant features
+from this language model are what make BERT so powerful once it's fine-tuned.
+Training the student network on BERT's output thus allows some of this
+``outside knowledge'' to percolate toward the student network.
 
-To provide a concrete example of how this might work, suppose BERT captures from
-its pre-training that ``bad'', ``horrible,'' and ``terrible'' are approximate
-synonyms. In a sentiment task, these three words appear in three different
-sentences, two of which are negative, and one of which is positive. A fine-tuned
-BERT may provide a lower likelihood of being positive to the positive sentence
-than it would otherwise even if
+To provide a concrete example of how this might work, suppose BERT captures
+from its pre-training that ``bad'', ``horrible,'' and ``terrible'' are
+approximate synonyms. In a sentiment task, these three words appear in three
+different sentences, two of which are negative, and one of which is positive.
+A fine-tuned BERT may provide a lower likelihood of being positive to the
+positive sentence than it would otherwise even if
 
@@
 
-We first set up some notation. Let $F_\btheta = G_\bpsi \circ \bert_\bphi$ be a
-transformed model where
-$\btheta = (\bphi, \bpsi)$ be parameters of the subparts of the model.
-$\bert_\bphi$ is a BERT model where the pretrained weights are $\bphi_0 = 
-(\bphi_0^i)_{i=1}^n$, and
-$G_\bpsi$ is additional layers for fine-tuning BERT, parameterized by $\bpsi$.
-We decompose the subparts of the model into layers: \begin{align*}
+We first set up some notation. Let $F_\btheta = G_\bpsi \circ \bert_\bphi$ be
+a transformed model where $\btheta = (\bphi, \bpsi)$ be parameters of the
+subparts of the model. $\bert_\bphi$ is a BERT model where the pretrained
+weights are $\bphi_0 = (\bphi_0^i)_{i=1}^n$, and $G_\bpsi$ is additional
+layers for fine-tuning BERT, parameterized by $\bpsi$. We decompose the
+subparts of the model into layers: \begin{align*}
 \bert_\bphi &= f_{n}^{\bphi_n} \circ \cdots \circ f_1^{\bphi_1} \\
@@
 \]
-for some loss function specific to the task. For instance, $\ell$ is cross-entropy
-loss for a (multiclass) classification problem, and $\ell$ is mean-squared-error
-for a regression problem, which correspond to log-likelihoods in Categorical and
-Gaussian models, respectively. The innovation of DeepTwist-based training is
-perturbing the usual gradient-based optimization by repeatedly distorting the
-current weights to achieve compression objectives.
+for some loss function specific to the task. For instance, $\ell$ is
+cross-entropy loss for a (multiclass) classification problem, and $\ell$ is
+mean-squared-error for a regression problem, which correspond to
+log-likelihoods in Categorical and Gaussian models, respectively. The
+innovation of DeepTwist-based training is perturbing the usual gradient-based
+optimization by repeatedly distorting the current weights to achieve
+compression objectives.
 
-Specifically, the DeepTwist framework presented in \Cref{sec:training} applies a
-distortion
-step for fixed intervals during training, where \[
+Specifically, the DeepTwist framework presented in \Cref{sec:training} applies
+a distortion step for fixed intervals during training, where \[
 \btheta \gets \distortion(\btheta). 
@@
 i.e. \begin{align*}
-\distortion'(\btheta) &= \\ (&\distortion(\bphi_1),\ldots,\distortion(\bphi_n),\\
+\distortion'(\btheta) &= \\
+(&\distortion(\bphi_1),\ldots,\distortion(\bphi_n),\\
 &\distortion(\bpsi_1),\ldots, \distortion(\bpsi_m)).
@@
 
-  Pruning is an extremely simple procedure. When $p$ is large, say, $p=0.99$, we
-  may take advantage of sparsity of the resulting model by saving locations of
-  nonzero entries, and thus reducing the model size in memory. However, such
-  compression does not come without potential sacrifices to computational speed,
-  as computation needed to be carried out on sparse data structures, which may
-  not effectively make use of standard hardware.
+  Pruning is an extremely simple procedure. When $p$ is large, say, $p=0.99$,
+  we may take advantage of sparsity of the resulting model by saving locations
+  of nonzero entries, and thus reducing the model size in memory. However,
+  such compression does not come without potential sacrifices to computational
+  speed, as computation needed to be carried out on sparse data structures,
+  which may not effectively make use of standard hardware.
 
-  Pruning is an out-of-the-box procedure that works with any models. However, as
-  a price of the generality, pruning fails to be tailored to the nature of BERT
-  being a pre-trained model. Suppose the pretrained weights $\bphi_0 $ capture
-  certain structure of language, then dramatic distortions to $\bphi_0$
-  essentially discards the information, especially early in the training loop.
-  We may partially remedy this issue by either using a dynamic pruning rate,
-  where pruning rate is small early in the training loop or by using
-  layer-specific pruning rates, with layers in $\bert$ having a lower pruning
-  rate than layers in $G$.
+  Pruning is an out-of-the-box procedure that works with any models. However,
+  as a price of the generality, pruning fails to be tailored to the nature of
+  BERT being a pre-trained model. Suppose the pretrained weights $\bphi_0 $
+  capture certain structure of language, then dramatic distortions to
+  $\bphi_0$ essentially discards the information, especially early in the
+  training loop. We may partially remedy this issue by either using a dynamic
+  pruning rate, where pruning rate is small early in the training loop or by
+  using layer-specific pruning rates, with layers in $\bert$ having a lower
+  pruning rate than layers in $G$.
 
   A direct approach to taking advantage of pretrained models, however, is
-  \emph{difference pruning}, where we ensure that
-  the difference between the model and a pretrained model is sparse.
-  Effectively, difference pruning ensures a form of weight sharing between
-  various BERT-based models for different tasks.
+  \emph{difference pruning}, where we ensure that the difference between the
+  model and a pretrained model is sparse. Effectively, difference pruning
+  ensures a form of weight sharing between various BERT-based models for
+  different tasks.
 
@@
 Observe that difference pruning provides no compression benefits when there is
-only one fine-tuning task; however, when the number of potential tasks is large,
-we only need to save $\btheta_0$ and the sparse matrix $\btheta - \btheta_0,$
-and $\btheta_0$ is shared across tasks.
+only one fine-tuning task; however, when the number of potential tasks is
+large, we only need to save $\btheta_0$ and the sparse matrix $\btheta -
+\btheta_0,$ and $\btheta_0$ is shared across tasks.
 
-Observe that we can transform any reduction technique by applying the reduction
-technique on the difference, and thus the \emph{difference} should be viewed 
-(and is implemented) as a decorator to a conventional distortion technique.
+Observe that we can transform any reduction technique by applying the
+reduction technique on the difference, and thus the \emph{difference} should
+be viewed (and is implemented) as a decorator to a conventional distortion
+technique.
 
@@
 
-\begin{figure}
-  \centering
-  \missingfigure[figheight=8cm]{}
-  \caption{\label{fig:diagram} This is a good place to include a diagram showing how your model works. Examples include a graphical model or a neural network block diagram.}
-\end{figure}
+% \begin{figure}
+%   \centering
+%   \missingfigure[figheight=8cm]{}
+%   \caption{\label{fig:diagram} This is a good place to include a diagram showing how your model works. Examples include a graphical model or a neural network block diagram.}
+% \end{figure}
 

### 2019-05-12 util_funcs.py
Testing code

@@ -236,16 +236,16 @@ def get_dataloader(
 
 
 
-def get_optimizer(model, learning_rate, warmup_proportion, 
+def get_optimizer(model, learning_rate, warmup_proportion,
                   num_train_optimization_steps, **kwargs):
     param_optimizer = list(model.named_parameters())
     no_decay = ['bias', 'LayerNorm.bias', 'LayerNorm.weight']
     optimizer_grouped_parameters = [
-        {'params': [p for n, p in param_optimizer 
-                    if not any(nd in n for nd in no_decay)], 
+        {'params': [p for n, p in param_optimizer
+                    if not any(nd in n for nd in no_decay)],
          'weight_decay': 0.01},
-        {'params': [p for n, p in param_optimizer 
-                    if any(nd in n for nd in no_decay)], 
+        {'params': [p for n, p in param_optimizer
+                    if any(nd in n for nd in no_decay)],
          'weight_decay': 0.0}
         ]
     optimizer = BertAdam(optimizer_grouped_parameters,
@@ -259,10 +259,11 @@ def get_data(processor, runtime_config, **kwargs):
     label_list, num_labels, tokenizer, train_examples, num_train_optimization_steps = \
     process_data(processor, **runtime_config, **kwargs)
 
-    train_dataloader = get_dataloader(train_examples, label_list, 
+    train_dataloader = get_dataloader(train_examples, label_list,
                    tokenizer, **runtime_config, **kwargs)
     return label_list, num_labels, tokenizer, train_examples, \
            num_train_optimization_steps, train_dataloader
+
 
 def get_log_name():
     import pytz
@@ -270,8 +271,8 @@ def get_log_name():
     now = datetime.now(tz=pytz.UTC)
     now_est = now.astimezone(pytz.timezone('America/New_York'))
     return now_est.strftime('%Y-%m-%d_%H_%M')
-     
-    
+
+
 def save_model(model, output_dir):
     # Save a trained model and the associated configuration
     model_to_save = model.module if hasattr(model, 'module') else model  # Only save the model it-self

### 2019-05-12 paper/paper.tex
Testing code
Add introduction and result tables

@@
-\documentclass[11pt]{article}
+\documentclass[10pt]{article}
 
@@
 
-Example Structure:
-\begin{itemize}
-\item What is the problem of interest and what (high-level) are the current best methods for solving it?
-\item How do you plan to improve/understand/modify this or related methods?
-\item Preview your research process, list the contributions you made, and summarize your experimental findings.
-\end{itemize}
+% Example Structure:
+% \begin{itemize}
+% \item What is the problem of interest and what (high-level) are the current best methods for solving it?
+% \item How do you plan to improve/understand/modify this or related methods?
+% \item Preview your research process, list the contributions you made, and summarize your experimental findings.
+% \end{itemize}
+
+Deep Neurel Networks (DDNs) have evolved to the state-of-art for many tasks in
+language modeling. In the meantime, they have become increasingly large in
+size, due to both pre-trained embeddings and deeper networks. However, in
+order to deploy the models on more resource-conscious devices efficiently,
+such as mobile devices or even older personal laptops, as opposed to on cloud
+virtual machines, it is crucial to reduce the size of the models.
+
+Previous work has had a lot of success in computer vision tasks.
+\citet{han2015deep} was able to reduce the size of AlexNet by 35$\times$ and
+the size of VGG-16 by 49$\times$ without loss of accuracy. Recently, similar
+compression techniques were applied by \citet{cheong2014transformer} on
+Transformers and reduced the size by a factor of 5.85 while retaining 98.43\%
+of the performance. To the best of our knowledge, compressing language models
+remains an under-studied field.
+
+In this paper, we proved that DeepTwist framework works well on compressing
+language models with pruning. {\color{red} TODO: prune99 result}.
+
+proposed weight-sharing method Difference Pruning
+
+attempt kd but does not work well
 
@@
 
-Deep Neurel Networks (DNNs) have become extremely large in size with growing
-complexities. A BERT base model has 110M parameters and takes 438 MB disk space
-to store. This makes it very hard to deploy those models on mobile devices,
-which in most cases have limited storage and RAM and lower computational
-resources. As a result, we are not able to store multiple models for different
-tasks on mobile devices, and evaluating one single model also takes too much
-time due to computational capacity limit. The challenge that we are facing is
-how to compress DNNs in size while keeping their predictive performance
-competitive with full model.
+DNNs have become extremely large in size with growing complexities. A BERT
+base model has 110M parameters and takes 438 MB disk space to store. This
+makes it very hard to deploy those models on mobile devices, which in most
+cases have limited storage and RAM and low computational resources. As a
+result, we are not able to store multiple models for different tasks on mobile
+devices. Allocating hundreds of megabytes to to those models is also not
+realistic for mobile apps such as Gmail or Facebook. And due to increasing
+privacy concerns, users prefer models generating predictions based on their
+input to be running locally instead of sending information to the cloud. Last
+but not least, evaluating enormous models takes too much time on mobile
+devices and can drain batteries significantly.
+
+The challenge that we are facing is therefore how to compress DNNs in size
+while keeping their predictive performance competitive with full model.
+
+% Though these neural networks are very powerful, the
+% large number of weights consumes considerable storage and memory bandwidth.
+For example, the AlexNet Caffemodel is over 200MB, and the VGG-16 Caffemodel is over 500MB (BVLC).
+This makes it difficult to deploy deep neural networks on mobile system.
+% First, for many mobile-first companies such as Baidu and Facebook, various apps are updated via different app stores, and they are very sensitive to the size of the binary files.
+For example, App Store has the restriction “apps above 100 MB will not download until you connect to Wi-Fi”.
+As a result, a feature that increases the binary size by 100MB will receive much more scrutiny than one that increases it by 10MB.
+Although having deep neural networks running on mobile has many great
 
@@
 We are interested in compressing the language representation model BERT
-\citep{devlin2018bert}.  It is the state-of-art result in many natural language
-processing tasks  such as natural language inference, paraphrasing and named
-entity recognition.
+\citep{devlin2018bert}.  It is the state-of-art result in many natural
+language processing tasks  such as natural language inference, paraphrasing
+and named entity recognition.
 
@@
 
-DeepTwist, a end-to-end training framework, allows us to incorporate compression
-procedures into training \citep{lee2018deeptwist}. Under this framework, the
-model parameters are occasionally distorted during training time instead of only
-at the end. This framework has the benefit of simplified training procedure and
-faster convergence and reduced requirement for hyperparameter tuning. Experiment
-on MNIST dataset with DeepTwist shows that LeNet-5 and LeNet-300-100 models are
-able to retain predictive accuracy under high compression rate.
+DeepTwist, a end-to-end training framework, allows us to incorporate
+compression procedures into training \citep{lee2018deeptwist}. Under this
+framework, the model parameters are occasionally distorted during training
+time instead of only at the end. This framework has the benefit of simplified
+training procedure and faster convergence and reduced requirement for
+hyperparameter tuning. Experiment on MNIST dataset with DeepTwist shows that
+LeNet-5 and LeNet-300-100 models are able to retain predictive accuracy under
+high compression rate.
 
@@
 
-% \begin{table}
-%   \centering
-%   \missingfigure[figheight=5cm]{}
-%   \caption{Secondary table or figure in results section.}
-%   \label{fig:mainres}
-% \end{table}
+\begin{table}[tbh]
+        \caption{Results for DeepTwist}
+        \label{tab:deeptwist_results}
+        \centering
+        \vspace{1em}
+        \begin{tabular}{lccccc}
+\toprule
+{} &               type &  param &  val loss &   val acc \\
+{} & 
+\hypertarget{tabcol:1}{(1)} & \hypertarget{tabcol:2}{(2)} & \hypertarget{tabcol:3}{(3)} & \hypertarget{tabcol:4}{(4)} \\ \midrule
+0  &  diff prune global &   $90$ &   $0.211$ &   $0.912$ \\
+1  &              prune &   $20$ &   $0.291$ &   $0.886$ \\
+2  &              prune &   $80$ &   $0.532$ &   $0.767$ \\
+3  &         diff prune &   $80$ &   $0.222$ &   $0.916$ \\
+4  &  diff prune global &   $99$ &       --- &       --- \\
+5  &  diff prune global &   $90$ &   $0.213$ &   $0.916$ \\
+6  &         diff prune &   $40$ &   $0.203$ &   $0.909$ \\
+7  &                svd &   $50$ &   $0.490$ &   $0.810$ \\
+8  &                svd &  $200$ &   $0.459$ &   $0.845$ \\
+9  &              prune &   $40$ &   $0.424$ &   $0.845$ \\
+10 &              prune &   $60$ &   $0.425$ &   $0.815$ \\
+11 &  diff prune global &   $99$ &   $0.230$ &   $0.901$ \\
+12 &  diff prune global &   $99$ &   $0.222$ &   $0.905$ \\
+13 &         diff prune &   $99$ &   $0.222$ &   $0.913$ \\
+14 &         diff prune &   $95$ &   $0.221$ &   $0.916$ \\
+15 &         diff prune &   $90$ &   $0.216$ &   $0.916$ \\
+16 &         diff prune &   $60$ &   $0.209$ &   $0.920$ \\
+17 &                svd &  $100$ &   $0.515$ &   $0.823$ \\
+18 &                svd &  $150$ &   $0.456$ &   $0.828$ \\
+19 &         diff prune &   $80$ &   $2.533$ &   $0.491$ \\
+20 &         diff prune &   $90$ &       --- &       --- \\
+21 &  diff prune global &    $0$ &   $0.738$ &   $0.509$ \\
+22 &         diff prune &    $0$ &   $0.692$ &   $0.522$ \\
+23 &         diff prune &    $0$ &   $1.854$ &   $0.491$ \\
+\bottomrule
+\end{tabular}
+
+\end{table}
+
+\begin{table}[tbh]
+        \caption{Results for Knowledge Distillation}
+        \label{tab:kd_results}
+        \centering
+        \vspace{1em}
+        \begin{tabular}{lccccccc}
+\toprule
+{} &  framework &  type &  val loss &  ß val acc \\
+{} & \hypertarget{tabcol:1}{(1)} & \hypertarget{tabcol:2}{(2)} & \hypertarget{tabcol:3}{(3)} & \hypertarget{tabcol:4}{(4)} \\
+\midrule
+0 &        nokd &   CNN &   $0.906$ &   $0.799$ \\
+1 &        nokd &   CNN &   $0.448$ &   $0.784$ \\
+2 &        nokd &   CNN &   $0.856$ &   $0.812$ \\
+3 &          kd &  LSTM &   $0.738$ &   $0.831$ \\
+4 &          kd &   CNN &   $0.423$ &   $0.834$ \\
+\bottomrule
+\end{tabular}
+
+\end{table}
 

### 2019-05-12 paper/paper.tex
Remove floating 'HEAD' in paper.tex

@@
   \begin{itemize}
-  \item This document describes the expected style, structure, and rough proportions for your final project write-up.
-  \item While you are free to break from this structure, consider it a strong prior for our expectations of the final report.
-\item Length is a hard constraint.
-You are only allowed max \textbf{8 pages} in this format.
-While you can include supplementary material, it will not be factored into the grading process.
-It is your responsibility to convey the main contributions of the work in the length given.
+  \item This document describes the expected style, structure, and rough
+  proportions for your final project write-up.
+  \item While you are free to break from this structure, consider it a strong
+  prior for our expectations of the final report.
+  \item Length is a hard constraint. You are only allowed max \textbf{8 pages}
+  in this format. While you can include supplementary material, it will not be
+  factored into the grading process. It is your responsibility to convey the
+  main contributions of the work in the length given.
   \end{itemize}
@@
 
-Deep Neurel Networks (DDNs) have evolved to the state-of-art for many tasks in
+Deep Neural Networks (DDNs) have evolved to the state-of-art for many tasks in
 language modeling. In the meantime, they have become increasingly large in
@@
 % \item What data exists for this problem?
-% \item What are the challenges/opportunities inherent to the data? (High dimensional, sparse, missing data, noise, structure, discrete/continuous, etc?)
+% \item What are the challenges/opportunities inherent to the data? (High
+% dimensional, sparse, missing data, noise, structure, discrete/continuous,
+% etc?)
 % \end{itemize}
@@
 The benefits of training in this fashion have been empirically documented
-% TODO: paper on KD doing well? 
-\citep{hinton2015distilling}
-and have theoretical motivation. Our goal of any network is to learn the
-conditional distribution 
+\citep{hinton2015distilling} and have theoretical motivation. Our goal of any
+network is to learn the conditional distribution 
 \[ p(y_i = k \mid \bm{x}_i).\]
@@
 A fine-tuned BERT may provide a lower likelihood of being positive to the
-positive sentence than it would otherwise even if
-
-% TODO: KD benefits
+positive sentence than it would otherwise even if the word of interest appears
+nowhere else.
 
 For our knowledge distillation, we make use of a fine-tuned BERT on a task as
-our teacher network and train a simpler model to emulate the predictions use
-\nameref{sec:model}
-
-% TODO: talk about KD
+our teacher network and train a simpler model to emulate the predictions. For
+the student network, we use both a CNN and an LSTM, specified further in
+\cref{sec:model}.
 
@@
 
-% TODO: talk about DeepTwist™
+Knowledge distillation operates by passing knowledge from a teacher network to a
+student network. There is no requirement that these networks resemble each other
+in any way. We may, however, wish to directly compress a model whose
+architecture we've had success with.
 
-\begin{comment}
-\begin{itemize}
-\item How do you plan on training your parameters / inferring the
-  states of your latent variables (MLE / MAP / Backprop / VI / EM / BP / ...)
-
-\item What are the assumptions implicit in this technique? Is it an approximation or exact? If it is an approximation what bound does it optimize?
-
-\item What is the explicit method / algorithm that you derive for learning these parameters?
-\end{itemize}
-\end{comment}
+To this end, we follow the framework put forward by \citet{lee2018deeptwist},
+\emph{DeepTwist}, whose training loop is characterized by \cref{algo:deeptwist}.
+Training of the model closely resembles SGD with one important modification:
+every $S_d$ batches, the model weights are transformed by a \emph{distortion}
+function.
 
@@
   \begin{algorithmic}
-    \STATE{}
+    \STATE{$n \leftarrow$ number of batches per epoch}
+    \STATE{$\theta \leftarrow$ initialization of model parameters}
+    \STATE{$k \leftarrow$ number of epochs to train}
+    \STATE{$S_d \leftarrow$ distortion step}
+    \FOR{$i=0$ to $k \cdot n$}
+      \STATE{batch $\leftarrow$ batches[$i \pmod n$]}
+      \STATE{$\theta \leftarrow \theta - \eta \nabla \ell(\theta,
+      \text{batch})$}
+      \COMMENT{gradient step}
+      \IF{$i \equiv 0 \pmod{S_d}$}
+        \STATE{$\theta \leftarrow \distortion(\theta)$}
+      \ENDIF
+    \ENDFOR
+    \STATE{$\theta \leftarrow \distortion(\theta)$}
   \end{algorithmic}
-  \caption{Your Pseudocode}
+  \caption{DeepTwist Training Loop}
+  \label{algo:deeptwist}
 \end{algorithm}
+
+We have significant flexibility in picking a distortion function, but in order
+to be useful, it must provide compression benefits. That is, the image of the
+distortion function should have a parameterization that takes less space in
+memory than then range of all possible $\theta$s. For example, if $\theta \in
+\mathbb{R}^{m,n}$, and the distortion produces a matrix of rank 1, then any
+distorted matrix could be uniquely identified by $\theta' \in \mathbb{R}^{n+m}$
+through a matrix factorization.
+
+It is important to note that while $\theta$ will be compressible immediately
+after a distortion step, there is no guarantee that it will remain so after some
+gradient steps. In fact, almost surely it will not be. Thus, we also enforce
+that the process ends on a distortion step.
 
@@
 % \item What is the formal definition of your problem?
-% \item What is the precise mathematical model you are using to represent it? In almost all cases this will use the probabilistic language from class, e.g.
+% \item What is the precise mathematical model you are using to represent it? In
+% almost all cases this will use the probabilistic language from class, e.g.
 %   \begin{equation}
@@
 
-% \item What are the parameters or latent variables of this model that you plan on estimating or inferring?
-Be explicit.
-How many are there?
-Which are you assuming are given?
-How do these relate to the original problem description?
+% \item What are the parameters or latent variables of this model that you plan
+% on estimating or inferring? Be explicit. How many are there? Which are you
+% assuming are given? How do these relate to the original problem description?
 % \end{itemize}
@@
 %   \missingfigure[figheight=8cm]{}
-%   \caption{\label{fig:diagram} This is a good place to include a diagram showing how your model works. Examples include a graphical model or a neural network block diagram.}
+%   \caption{\label{fig:diagram} This is a good place to include a diagram
+%   showing how your model works. Examples include a graphical model or a neural
+%   network block diagram.}
 % \end{figure}
@@
 \subsection{Knowledge Distillation}
-For knowledge distillation experiments, we use various configurations of
-the student network:
-\paragraphdot{LSTM} We use a one-layer LSTM network with hidden dimension
-$H=200$. We first embed the one-hot representation of tokens, and we feed
-the embeddings through an LSTM. We then map the last hidden state of the
-LSTM through a linear layer for classification. 
-\paragraphdot{CNN} We use an implementation\footnote{\url{https://github.com/jfilter/cnn-text-classification-pytorch/blob/master/cnn_text_classification/model.py}} 
+
+For knowledge distillation experiments, we use various configurations of the
+student network: \paragraphdot{LSTM} We use a one-layer LSTM network with hidden
+dimension $H=200$. We first embed the one-hot representation of tokens, and we
+feed the embeddings through an LSTM. We then map the last hidden state of the
+LSTM through a linear layer for classification.  \paragraphdot{CNN} We use an
+implementation\footnote{\url{https://github.com/jfilter/cnn-text-classification-pytorch/blob/master/cnn_text_classification/model.py}}
 of \citet{kim2014convolutional} with kernel sizes $(3,4,5)$, hidden size
-$H=300$, no dropout, and $20$ kernels for each kernel size.\footnote{These
-are default in the implementation we used.}
+$H=300$, no dropout, and $20$ kernels for each kernel size.\footnote{These are
+default in the implementation we used.}
 
@@
 \begin{itemize}
-\item What were the results comparing previous work / baseline systems / your systems on the main task?
+\item What were the results comparing previous work / baseline systems / your
+systems on the main task?
 \item What were the secondary results comparing the variants of your system?
-\item This section should be fact based and relatively dry. What happened, what was significant?
+\item This section should be fact based and relatively dry. What happened, what
+was significant?
 \end{itemize}
@@
 %   \missingfigure{}
-%   \caption{This is usually a table. Tables with numbers are generally easier to read than graphs, so prefer when possible.}
+%   \caption{This is usually a table. Tables with numbers are generally easier
+%   to read than graphs, so prefer when possible.}
 %   \label{fig:mainres}
@@
 
-\begin{table}[tbh]
-        \caption{Results for DeepTwist}
-        \label{tab:deeptwist_results}
-        \centering
-        \vspace{1em}
-        \begin{tabular}{lccccc}
-\toprule
-{} &               type &  param &  val loss &   val acc \\
-{} & 
-\hypertarget{tabcol:1}{(1)} & \hypertarget{tabcol:2}{(2)} & \hypertarget{tabcol:3}{(3)} & \hypertarget{tabcol:4}{(4)} \\ \midrule
-0  &  diff prune global &   $90$ &   $0.211$ &   $0.912$ \\
-1  &              prune &   $20$ &   $0.291$ &   $0.886$ \\
-2  &              prune &   $80$ &   $0.532$ &   $0.767$ \\
-3  &         diff prune &   $80$ &   $0.222$ &   $0.916$ \\
-4  &  diff prune global &   $99$ &       --- &       --- \\
-5  &  diff prune global &   $90$ &   $0.213$ &   $0.916$ \\
-6  &         diff prune &   $40$ &   $0.203$ &   $0.909$ \\
-7  &                svd &   $50$ &   $0.490$ &   $0.810$ \\
-8  &                svd &  $200$ &   $0.459$ &   $0.845$ \\
-9  &              prune &   $40$ &   $0.424$ &   $0.845$ \\
-10 &              prune &   $60$ &   $0.425$ &   $0.815$ \\
-11 &  diff prune global &   $99$ &   $0.230$ &   $0.901$ \\
-12 &  diff prune global &   $99$ &   $0.222$ &   $0.905$ \\
-13 &         diff prune &   $99$ &   $0.222$ &   $0.913$ \\
-14 &         diff prune &   $95$ &   $0.221$ &   $0.916$ \\
-15 &         diff prune &   $90$ &   $0.216$ &   $0.916$ \\
-16 &         diff prune &   $60$ &   $0.209$ &   $0.920$ \\
-17 &                svd &  $100$ &   $0.515$ &   $0.823$ \\
-18 &                svd &  $150$ &   $0.456$ &   $0.828$ \\
-19 &         diff prune &   $80$ &   $2.533$ &   $0.491$ \\
-20 &         diff prune &   $90$ &       --- &       --- \\
-21 &  diff prune global &    $0$ &   $0.738$ &   $0.509$ \\
-22 &         diff prune &    $0$ &   $0.692$ &   $0.522$ \\
-23 &         diff prune &    $0$ &   $1.854$ &   $0.491$ \\
-\bottomrule
-\end{tabular}
+% \begin{table}[tbh]
+%         \caption{Results for DeepTwist}
+%         \label{tab:deeptwist_results}
+%         \centering
+%         \vspace{1em}
+%         \begin{tabular}{lccccc}
+% \toprule
+% {} &               type &  param &  val loss &   val acc \\
+% {} & 
+% \hypertarget{tabcol:1}{(1)} & \hypertarget{tabcol:2}{(2)} & \hypertarget{tabcol:3}{(3)} & \hypertarget{tabcol:4}{(4)} \\ \midrule
+% 0  &  diff prune global &   $90$ &   $0.211$ &   $0.912$ \\
+% 1  &              prune &   $20$ &   $0.291$ &   $0.886$ \\
+% 2  &              prune &   $80$ &   $0.532$ &   $0.767$ \\
+% 3  &         diff prune &   $80$ &   $0.222$ &   $0.916$ \\
+% 4  &  diff prune global &   $99$ &       --- &       --- \\
+% 5  &  diff prune global &   $90$ &   $0.213$ &   $0.916$ \\
+% 6  &         diff prune &   $40$ &   $0.203$ &   $0.909$ \\
+% 7  &                svd &   $50$ &   $0.490$ &   $0.810$ \\
+% 8  &                svd &  $200$ &   $0.459$ &   $0.845$ \\
+% 9  &              prune &   $40$ &   $0.424$ &   $0.845$ \\
+% 10 &              prune &   $60$ &   $0.425$ &   $0.815$ \\
+% 11 &  diff prune global &   $99$ &   $0.230$ &   $0.901$ \\
+% 12 &  diff prune global &   $99$ &   $0.222$ &   $0.905$ \\
+% 13 &         diff prune &   $99$ &   $0.222$ &   $0.913$ \\
+% 14 &         diff prune &   $95$ &   $0.221$ &   $0.916$ \\
+% 15 &         diff prune &   $90$ &   $0.216$ &   $0.916$ \\
+% 16 &         diff prune &   $60$ &   $0.209$ &   $0.920$ \\
+% 17 &                svd &  $100$ &   $0.515$ &   $0.823$ \\
+% 18 &                svd &  $150$ &   $0.456$ &   $0.828$ \\
+% 19 &         diff prune &   $80$ &   $2.533$ &   $0.491$ \\
+% 20 &         diff prune &   $90$ &       --- &       --- \\
+% 21 &  diff prune global &    $0$ &   $0.738$ &   $0.509$ \\
+% 22 &         diff prune &    $0$ &   $0.692$ &   $0.522$ \\
+% 23 &         diff prune &    $0$ &   $1.854$ &   $0.491$ \\
+% \bottomrule
+% \end{tabular}
 
-\end{table}
+% \end{table}
+
+\input{../tabs/deeptwist_table.tex}
 
@@
 \section{Discussion}
+Things to say about deeptwist
+\begin{itemize}
+  \item Stratified prune better
+  \item Prune rate mad robust
+  \item Diff gud
+  \item ``Improved performance''
+  \item QQP takes long, but looks okay
+  \item Didn't try only purning the $\bert$ part
+\end{itemize}
+
+Things to say about KD
+\begin{itemize}
+  \item it bad
+  \item doens't work
+  \item LSTM weird/CNN incrdibly noisy
+  \item \TODO{compare}
+\end{itemize}
 
@@
 \item What conclusions can you draw from the results section?
-\item Is there further analysis you can do into the results of the system? Here is a good place to include visualizations, graphs, qualitative analysis of your results.
+\item Is there further analysis you can do into the results of the system? Here
+is a good place to include visualizations, graphs, qualitative analysis of your
+results.
 

### 2019-05-12 paper/paper.tex
Fix misc typos
Add KD discussion

@@
 \end{tabular}
-
+\label{tbl:kdresults}
 \end{table}
@@
 \section{Discussion}
-Things to say about deeptwist
+
+Things to say about DeepTwist
 \begin{itemize}
@@
   \item QQP takes long, but looks okay
-  \item Didn't try only purning the $\bert$ part
+  \item Didn't try only pruning the $\bert$ part
 \end{itemize}
@@
   \item it bad
-  \item doens't work
-  \item LSTM weird/CNN incrdibly noisy
+  \item doesn't work
+  \item LSTM weird/CNN incredibly noisy
   \item \TODO{compare}
 \end{itemize}
+
+When compared to the performance of a fine-tuned BERT on SST-2, our Knowledge
+Distillation results---displayed in \cref{tbl:kdresults}---fall short. However,
+it is important to note the student networks are also much smaller than BERT. To
+isolate the effect of KD, we compare the performance of
+\citet{kim2014convolutional}'s CNN trained on the correct labels versus the BERT
+probabilities. This suggests a modest performance benefit of two percentage
+points in validation accuracy. However, we see no evidence of training being
+sped up by using KD.
+
+We also identify some curious behavior in the KD training curves. When training
+the LSTM on the BERT outputs, neither training loss nor validation loss decrease
+at first. In fact, they stay approximately constant for a couple of epochs. Only
+after this prolonged period does loss abruptly start going down, producing a
+normal curve from that point forward. We find this remarkably puzzling. We
+hypothesize this may be the effect of our adaptive learning rate starting out
+too low and taking multiple epochs to grow to a point where it can meaningfully
+update parameters. 
+% TODO: include this graph -- screenshot from tensorboard?
 

### 2019-05-12 paper/paper.tex
Write DeepTwist discussion section

@@
 
-Things to say about DeepTwist
-\begin{itemize}
-  \item Stratified prune better
-  \item Prune rate mad robust
-  \item Diff gud
-  \item ``Improved performance''
-  \item QQP takes long, but looks okay
-  \item Didn't try only pruning the $\bert$ part
-\end{itemize}
+Our most striking result is the robust performance of difference pruning. Even
+keeping upwards of 99\% of the weights unchanged gives us performance that is
+very competitive with the unrestricted model. Most of our experiments are on
+SST-2, but we see success with this method on QQP as well, suggesting that
+small changes to pre-trained BERT are sufficient for performance on a specific
+task.
 
-Things to say about KD
-\begin{itemize}
-  \item it bad
-  \item doesn't work
-  \item LSTM weird/CNN incredibly noisy
-  \item \TODO{compare}
-\end{itemize}
+As expected, pruning a higher proportion of the weights decreases performance,
+but we are happily surprised at the relatively low magnitude of this effect even
+at high prune rates. Pruning with a global threshold rather than in a
+stratified way produces distinctly worse results. We suspect this is due to
+weights in different layers having different magnitudes, making a global
+threshold have an undue effect on layers whose weights tend to be smaller. We
+confirm this heterogeneity in 
+% TODO: include box-plots of weights
+
+Our non-difference distortions are more sensitive to the compression parameter
+(whether prune rate or SVD rank). We find it difficult to achieve performance
+comparable to the uncompressed BERT with a significantly compressed model. Among
+the different distortion methods, we favor pruning for its computational
+simplicity, and see no evidence that SVD achieves better compression.
+
+% Things to say about DeepTwist
+% \begin{itemize}
+%   \item Stratified prune better
+%   \item Prune rate mad robust
+%   \item Diff gud
+%   \item ``Improved performance''
+%   \item QQP takes long, but looks okay
+%   \item Didn't try only pruning the $\bert$ part
+% \end{itemize}
+% 
+% Things to say about KD
+% \begin{itemize}
+%   \item it bad
+%   \item doesn't work
+%   \item LSTM weird/CNN incredibly noisy
+%   \item \TODO{compare}
+% \end{itemize}
 
@@
 
-\begin{itemize}
-\item What conclusions can you draw from the results section?
-\item Is there further analysis you can do into the results of the system? Here
-is a good place to include visualizations, graphs, qualitative analysis of your
-results.
-
-\item  What questions remain open? What did you think might work, but did not?
-\end{itemize}
+% \begin{itemize}
+% \item What conclusions can you draw from the results section?
+% \item Is there further analysis you can do into the results of the system? Here
+% is a good place to include visualizations, graphs, qualitative analysis of your
+% results.
+% 
+% \item  What questions remain open? What did you think might work, but did not?
+% \end{itemize}
 

### 2019-05-12 paper/paper.tex
Add tentative abstract bullet points

@@
 \begin{abstract}
+\raggedright
   \begin{itemize}
-  \item This document describes the expected style, structure, and rough
-  proportions for your final project write-up.
-  \item While you are free to break from this structure, consider it a strong
-  prior for our expectations of the final report.
-  \item Length is a hard constraint. You are only allowed max \textbf{8 pages}
-  in this format. While you can include supplementary material, it will not be
-  factored into the grading process. It is your responsibility to convey the
-  main contributions of the work in the length given.
+  \item We apply model compression results to fine-tuned BERT on multiclass
+  classification problems.
+  \item Knowledge distillation and DeepTwist-based compression techniques give
+  us moderate compression benefits for a commensurate decrease in model
+  performance.
+  \item We achieve our most compelling results from employing the DeepTwist
+  framework to share weights across BERT models fine-tuned for different tasks.
+  \item Our work demonstrates most weights need not change in the fine-tuning
+  process.
+%   \item This document describes the expected style, structure, and rough
+%   proportions for your final project write-up.
+%   \item While you are free to break from this structure, consider it a strong
+%   prior for our expectations of the final report.
+%   \item Length is a hard constraint. You are only allowed max \textbf{8 pages}
+%   in this format. While you can include supplementary material, it will not be
+%   factored into the grading process. It is your responsibility to convey the
+%   main contributions of the work in the length given.
   \end{itemize}

### 2019-05-12 paper/paper.tex
Nitpicks on introduction section

@@
 
-Deep Neural Networks (DDNs) have evolved to the state-of-art for many tasks in
-language modeling. In the meantime, they have become increasingly large in
-size, due to both pre-trained embeddings and deeper networks. However, in
-order to deploy the models on more resource-conscious devices efficiently,
+Deep Neural Networks (DDNs) have become the state-of-art for many tasks in
+language modeling. At the same time, they have become progressively larger in
+size, due to both pre-trained embeddings and deeper networks.
+% TODO: how do pre-trained embeddings make networks larger? -FR
+However, in order to deploy the models on more resource-constrained devices,
 such as mobile devices or even older personal laptops, as opposed to on cloud
@@
 \citet{han2015deep} was able to reduce the size of AlexNet by 35$\times$ and
-the size of VGG-16 by 49$\times$ without loss of accuracy. Recently, similar
-compression techniques were applied by \citet{cheong2014transformer} on
-Transformers and reduced the size by a factor of 5.85 while retaining 98.43\%
-of the performance. To the best of our knowledge, compressing language models
-remains an under-studied field.
+the size of VGG-16 by 49$\times$ without loss of accuracy.
+% TODO: this isn't computer vision, right? -FR
+Recently, similar compression techniques were applied by
+\citet{cheong2014transformer} on Transformers and reduced the size by a factor
+of 5.85 while retaining 98.43\% of the performance. To the best of our
+knowledge, compressing language models remains an under-studied field.
 
-In this paper, we proved that DeepTwist framework works well on compressing
-language models with pruning. {\color{red} TODO: prune99 result}.
+% TODO: should we mention the high-level strategies these papers use to compress
+% their respective models? -FR
+
+In this paper, we demonstrate that the DeepTwist framework works well on
+compressing language models with pruning. {\color{red} TODO: prune99 result}.
 

### 2019-05-12 paper/paper.tex
Wording change in KD section

@@
 different sentences, two of which are negative, and one of which is positive.
-A fine-tuned BERT may provide a lower likelihood of being positive to the
+A fine-tuned BERT may predict a lower likelihood of being positive to the
 positive sentence than it would otherwise even if the word of interest appears

### 2019-05-12 paper/paper.tex
Change table formatting to be more readable
Fix first bullet point
Add curious training curves into paper.tex

@@
   \begin{itemize}
-  \item We apply model compression results to fine-tuned BERT on multiclass
+  \item We apply model compression techniques to fine-tuned BERT on multiclass
   classification problems.
@@
 
-\input{../tabs/deeptwist_table.tex}
+\input{../tabs/hierarchical_deeptwist_table.tex}
 
@@
 threshold have an undue effect on layers whose weights tend to be smaller. We
-confirm this heterogeneity in 
-% TODO: include box-plots of weights
+confirm this heterogeneity in \cref{fig:weightsbylayer}.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=.5\textwidth]{../figs/value_by_layer.pdf}
+\caption{Weight distributions for five most/least variable layers}
+\label{fig:weightsbylayer}
+\end{figure}
 
@@
 
+\begin{figure*}[tb]
+\centering
+\includegraphics{../figs/kd_lstm_training.png}
+\caption{Training loss (left), val. loss (middle), and val. accuracy
+(right) for LSTM KD}
+\label{fig:<+label+>}
+\end{figure*}<++>
+
 % \begin{itemize}

### 2019-05-12 paper/paper.tex
Small fixes to training loss figure
Concatenate tables and incorporate into paper.tex

@@
 
-\begin{table}[tbh]
-        \caption{Results for Knowledge Distillation}
-        \label{tab:kd_results}
-        \centering
-        \vspace{1em}
-        \begin{tabular}{lccccccc}
-\toprule
-{} &  framework &  type &  val loss &  ß val acc \\
-{} & \hypertarget{tabcol:1}{(1)} & \hypertarget{tabcol:2}{(2)} & \hypertarget{tabcol:3}{(3)} & \hypertarget{tabcol:4}{(4)} \\
-\midrule
-0 &        nokd &   CNN &   $0.906$ &   $0.799$ \\
-1 &        nokd &   CNN &   $0.448$ &   $0.784$ \\
-2 &        nokd &   CNN &   $0.856$ &   $0.812$ \\
-3 &          kd &  LSTM &   $0.738$ &   $0.831$ \\
-4 &          kd &   CNN &   $0.423$ &   $0.834$ \\
-\bottomrule
-\end{tabular}
-\label{tbl:kdresults}
-\end{table}
+\input{../tabs/kd_table.tex}
+
+% \begin{table}[tbh]
+%         \caption{Results for Knowledge Distillation}
+%         \label{tab:kd_results}
+%         \centering
+%         \vspace{1em}
+%         \begin{tabular}{lccccccc}
+% \toprule
+% {} &  framework &  type &  val loss &  ß val acc \\
+% {} & \hypertarget{tabcol:1}{(1)} & \hypertarget{tabcol:2}{(2)} & \hypertarget{tabcol:3}{(3)} & \hypertarget{tabcol:4}{(4)} \\
+% \midrule
+% 0 &        nokd &   CNN &   $0.906$ &   $0.799$ \\
+% 1 &        nokd &   CNN &   $0.448$ &   $0.784$ \\
+% 2 &        nokd &   CNN &   $0.856$ &   $0.812$ \\
+% 3 &          kd &  LSTM &   $0.738$ &   $0.831$ \\
+% 4 &          kd &   CNN &   $0.423$ &   $0.834$ \\
+% \bottomrule
+% \end{tabular}
+% \label{tbl:kdresults}
+% \end{table}
 
@@
 When compared to the performance of a fine-tuned BERT on SST-2, our Knowledge
-Distillation results---displayed in \cref{tbl:kdresults}---fall short. However,
+Distillation results---displayed in \cref{tab:kd_results}---fall short. However,
 it is important to note the student networks are also much smaller than BERT. To
@@
 after this prolonged period does loss abruptly start going down, producing a
-normal curve from that point forward. We find this remarkably puzzling. We
-hypothesize this may be the effect of our adaptive learning rate starting out
-too low and taking multiple epochs to grow to a point where it can meaningfully
-update parameters. 
-% TODO: include this graph -- screenshot from tensorboard?
+normal curve from that point forward. We find this---depicted in
+\cref{fig:kdlstmloss}---remarkably puzzling. We hypothesize this may be the
+effect of our adaptive learning rate starting out too low and taking multiple
+epochs to grow to a point where it can meaningfully update parameters.
 
@@
 \centering
-\includegraphics{../figs/kd_lstm_training.png}
+\includegraphics[width=\textwidth]{../figs/kd_lstm_training.png}
 \caption{Training loss (left), val. loss (middle), and val. accuracy
 (right) for LSTM KD}
-\label{fig:<+label+>}
-\end{figure*}<++>
+\label{fig:kdlstmloss}
+\end{figure*}
 

### 2019-05-12 paper/paper.tex
Finish introduction and resolve comments

--- 2019-05-12 paper/paper.tex
@@
 language modeling. At the same time, they have become progressively larger in
-size, due to both pre-trained embeddings and deeper networks.
-% TODO: how do pre-trained embeddings make networks larger? -FR
-However, in order to deploy the models on more resource-constrained devices,
-such as mobile devices or even older personal laptops, as opposed to on cloud
-virtual machines, it is crucial to reduce the size of the models.
+size, due to both larger out-of-box pre-trained embeddings and deeper
+networks. However, in order to deploy the models on more resource-constrained
+devices, such as mobile devices or even older personal laptops, as opposed to
+on cloud virtual machines, it is crucial to reduce the size of the models.
 
 Previous work has had a lot of success in computer vision tasks.
-\citet{han2015deep} was able to reduce the size of AlexNet by 35$\times$ and
-the size of VGG-16 by 49$\times$ without loss of accuracy.
-% TODO: this isn't computer vision, right? -FR
-Recently, similar compression techniques were applied by
-\citet{cheong2014transformer} on Transformers and reduced the size by a factor
-of 5.85 while retaining 98.43\% of the performance. To the best of our
-knowledge, compressing language models remains an under-studied field.
+\citet{han2015deep} was able to combine pruning, quantization and Huffman
+coding to reduce the size of AlexNet by 35$\times$ and the size of VGG-16 by
+49$\times$ without loss of accuracy. Recently, similar compression techniques
+were applied by \citet{cheong2014transformer} on language models, Transformers
+in specific, and reduced the size by a factor of 5.85 while retaining 98.43\%
+of the performance. To the best of our knowledge, compressing language models
+still remains an under-studied field.
 
-% TODO: should we mention the high-level strategies these papers use to compress
-% their respective models? -FR
+In this paper, we demonstrate that the DeepTwist framework
+\citep{lee2018deeptwist} is applicable to compressing fine-tuned BERT
+\citep{devlin2018bert} on multiclass classification problems in addition to
+computer vision tasks, though the drop in performance is less negligible.
+Knowledge distillation also achieves the compression objective with more than
+desired decrease in predictive accuracy.
 
-In this paper, we demonstrate that the DeepTwist framework works well on
-compressing language models with pruning. {\color{red} TODO: prune99 result}.
+We used two of the GLUE datasets SST-2 and QQP. We ran most of the experiments
+on SST-2, a binary sentiment classification task on single-sentence movie
+reviews. We validated the results on QQP, a binary classification task for
+whether two questions asked on Quora are semantically equivalent.
 
-proposed weight-sharing method Difference Pruning
-
-attempt kd but does not work well
+The most important contribution of this paper is that we proposed a new
+weight-sharing method called ``Difference Pruning'' which imposes constraint on
+the sparcity of weight difference with the pre-trained BERT model. While
+uncompressed fine-tuned BERT model achieves 92.9\% validation accuracy on
+SST-2, the Difference Pruning model that keeps 99\% of the pre-trained BERT
+weights achieves 91.3\% on the validation set. This enables multiple language
+modeling tasks to share the weights of pre-trained BERT and each incurs minimal
+extra storage space requirements.
 
@@
 while keeping their predictive performance competitive with full model.
-
-% Though these neural networks are very powerful, the
-% large number of weights consumes considerable storage and memory bandwidth.
-For example, the AlexNet Caffemodel is over 200MB, and the VGG-16 Caffemodel is over 500MB (BVLC).
-This makes it difficult to deploy deep neural networks on mobile system.
-% First, for many mobile-first companies such as Baidu and Facebook, various apps are updated via different app stores, and they are very sensitive to the size of the binary files.
-For example, App Store has the restriction “apps above 100 MB will not download until you connect to Wi-Fi”.
-As a result, a feature that increases the binary size by 100MB will receive much more scrutiny than one that increases it by 10MB.
-Although having deep neural networks running on mobile has many great
 

### 2019-05-12 paper/paper.tex

@@
 after this prolonged period does loss abruptly start going down, producing a
-normal curve from that point forward. We find this remarkably puzzling. We
-hypothesize this may be the effect of our adaptive learning rate starting out
-too low and taking multiple epochs to grow to a point where it can meaningfully
-update parameters. 
-% TODO: include this graph -- screenshot from tensorboard?
+normal curve from that point forward. We find this---depicted in
+\cref{fig:kdlstmloss}---remarkably puzzling. We hypothesize this may be the
+effect of our adaptive learning rate starting out too low and taking multiple
+epochs to grow to a point where it can meaningfully update parameters.
+
+\begin{figure*}[tb]
+\centering
+\includegraphics[width=\textwidth]{../figs/kd_lstm_training.png}
+\caption{Training loss (left), val. loss (middle), and val. accuracy
+(right) for LSTM KD}
+\label{fig:kdlstmloss}
+\end{figure*}
 

### 2019-05-13 paper/paper.tex
Add todo on outside data
Removing abstract bullet points

@@
 \begin{abstract}
-\raggedright
-  \begin{itemize}
-  \item We apply model compression techniques to fine-tuned BERT on multiclass
-  classification problems.
-  \item Knowledge distillation and DeepTwist-based compression techniques give
+% \raggedright
+  We apply model compression techniques to fine-tuned BERT on multiclass
+  classification problems.  Knowledge distillation and DeepTwist-based compression techniques give
   us moderate compression benefits for a commensurate decrease in model
-  performance.
-  \item We achieve our most compelling results from employing the DeepTwist
-  framework to share weights across BERT models fine-tuned for different tasks.
-  \item Our work demonstrates most weights need not change in the fine-tuning
+  performance. We achieve our most compelling results from employing the DeepTwist
+  framework to share weights across BERT models fine-tuned for different tasks. Our work demonstrates most weights need not change in the fine-tuning
   process.
@@
 %   main contributions of the work in the length given.
-  \end{itemize}
+  % \end{itemize}
 
@@
 
-\subsection{Deep Twist}
+\subsection{DeepTwist}
 
@@
 early stopping in training, with patience of 1 epoch, and early stopping is
-guided by validation error.
+guided by validation loss.
 
@@
 
-\begin{itemize}
-\item What were the results comparing previous work / baseline systems / your
-systems on the main task?
-\item What were the secondary results comparing the variants of your system?
-\item This section should be fact based and relatively dry. What happened, what
-was significant?
-\end{itemize}
+We show our results in \Cref {tab:deeptwist_results,tab:kd_results}. In the top
+pane of \Cref {tab:deeptwist_results}, we show the result of various
+DeepTwist-based compression techniques on the sentiment classification task,
+SST-2, stratifying by method and then by parameter of the method. Difference
+pruning, pruning, and rank reduction are implemented as \emph{distortion by
+layer} (see \Cref{sec:model}), where as ``difference pruning (global)''
+indicates difference pruning, but pooling all parameter values from all layers.
+The bottom pane of \Cref{tab:deeptwist_results} shows the performance on QQP of
+some competitive-performing model setups on SST-2, which are all
+difference-pruning based. In \Cref{tab:kd_results}, we present some knowledge
+distillation experiments, with the student network being an LSTM or a CNN, with
+or without dropout \citep{kim2014convolutional}.
+
+For the most part, difference pruning seems to be robust to the pruning
+rate. As a sanity check, we include difference pruning with 100\% pruning
+rate, which is equivalent to BERT model without fine-tuning, and obtaining
+essentially uniform results on the validation set. Difference pruning also
+seems to outperform both ``first-order'' DeepTwist techniques, pruning and
+rank reduction, which is unsurprising as difference pruning uses more
+parameters and uses parameters that are pretrained. Difference pruning also
+seems to extend to other tasks in GLUE, as it retains its behavior in
+SST-2 to QQP, for the most part. Knowledge distillation seems less
+promising. While knowledge distillation
+slightly improves upon the model directly trained on data, it does not
+fully replicate the performance of the teacher network. We now discuss our
+results in detail.
+
+% \begin{itemize}
+% \item What were the results comparing previous work / baseline systems / your
+% systems on the main task?
+% \item What were the secondary results comparing the variants of your system?
+% \item This section should be fact based and relatively dry. What happened,
+% what was significant?
+% \end{itemize}
 
@@
 
+\begin{figure*}[htb]
+\centering
+\includegraphics[width=\textwidth]{../figs/kd_lstm_training.png}
+\caption{Training loss (left), val. loss (middle), and val. accuracy
+(right) for LSTM KD}
+\label{fig:kdlstmloss}
+\end{figure*}
+
 Our most striking result is the robust performance of difference pruning. Even
@@
 
-\begin{figure*}[tb]
-\centering
-\includegraphics[width=\textwidth]{../figs/kd_lstm_training.png}
-\caption{Training loss (left), val. loss (middle), and val. accuracy
-(right) for LSTM KD}
-\label{fig:kdlstmloss}
-\end{figure*}
-
 % \begin{itemize}
@@
 \section{Conclusion}
+
+% TODO: talk about bringing in outside data for KD
 

### 2019-05-13 paper/paper.tex
Compression ratio discussion in results

@@
 
-Deep Neural Networks (DDNs) have become the state-of-art for many tasks in
+Deep Neural Networks (DNNs) have become the state-of-art for many tasks in
 language modeling. At the same time, they have become progressively larger in
-size, due to both larger out-of-box pre-trained embeddings and deeper
+size, due to both larger out-of-box pretrained embeddings and deeper
 networks. However, in order to deploy the models on more resource-constrained
@@
 weight-sharing method called ``Difference Pruning'' which imposes constraint on
-the sparcity of weight difference with the pre-trained BERT model. While
+the sparcity of weight difference with the pretrained BERT model. While
 uncompressed fine-tuned BERT model achieves 92.9\% validation accuracy on
-SST-2, the Difference Pruning model that keeps 99\% of the pre-trained BERT
+SST-2, the Difference Pruning model that keeps 99\% of the pretrained BERT
 weights achieves 91.3\% on the validation set. This enables multiple language
-modeling tasks to share the weights of pre-trained BERT and each incurs minimal
+modeling tasks to share the weights of pretrained BERT and each incurs minimal
 extra storage space requirements.
@@
 An additional benefit from knowledge distillation arises from BERT's
-pre-training. Because BERT is pre-trained on large amounts of unstructured
+pre-training. Because BERT is pretrained on large amounts of unstructured
 data, it contains a powerful language model which likely would be impossible
@@
   as a price of the generality, pruning fails to be tailored to the nature of
-  BERT being a pre-trained model. Suppose the pretrained weights $\bphi_0 $
+  BERT being a pretrained model. Suppose the pretrained weights $\bphi_0 $
   capture certain structure of language, then dramatic distortions to
@@
 a compression rate of \[
-\rho = \frac{r(n+m)}{2mn}.
+\rho = 1-\frac{r(n+m)}{2mn}.
 \]
@@
 
+Pruning admits a simple upper bound for compression, which is simply the
+pruning ratio.\footnote{The exact compression rate is complicated, due to
+the sparse data structure implemented for the compressed model} Compression
+rate for difference pruning depends on the number of tasks the user
+desires to perform, since difference pruning is understood to be a form of
+weight sharing. In that context, the (upper bound) compression rate of
+difference
+pruning
+is also self-evident. The compression rate achieved by rank reduction is \[
+\rho = 1 - \frac{r(n+m)}{2mn}.
+\]
+Since most matrices in \texttt{BERT-base-uncased} is $768\times 768,$ the
+compression rate is approximately \[
+\rho \approx 1 - \frac{r}{768} = (74.0\%,
+80.5\%,
+87.0\%,
+93.5\%)
+\]
+for $r = (200,150,100,50)$, respectively.
+
 For the most part, difference pruning seems to be robust to the pruning
@@
 SST-2, but we see success with this method on QQP as well, suggesting that
-small changes to pre-trained BERT are sufficient for performance on a specific
+small changes to pretrained BERT are sufficient for performance on a specific
 task.

### 2019-05-13 paper/paper.tex
Write draft of conclusion section

@@
 
-% TODO: talk about bringing in outside data for KD
+Knowledge Distillation displayed promise by improving student networks'
+performance versus training only on the classes $y_i$. However, the student
+networks fell short of replicating uncompressed BERT's performance. It is
+possible that future variations on our work could achieve competitive
+compression. In particular, we restrict our knowledge distillation only to the
+samples in the original training set. However, there is no need to perform
+training so narrowly since the teacher network can annotate any unsupervised
+data. It is likely that doing so would further increase performance, though we
+can only speculate as to the magnitude of the benefit.
 
-\begin{itemize}
-\item What happened?
-\item What next?
-\end{itemize}
+It is also possible that our choice of student network colored our results. We
+aimed for architectures known to work on SST-2 while being much smaller, such as
+\citet{kim2014convolutional}'s CNN. It is possible that we aimed too small and
+would be better served by a more complex model---possibly even a smaller version
+of BERT. Finally, in all our experiments our teacher network is a single
+fine-tuned version of BERT. Since teacher network complexity doesn't contribute
+to the complexity of the final model, we could instead use an ensemble of BERTs
+(or even other models) as our teacher network.
 
-% \section*{Acknowledgements}
+The DeepTwist framework---particularly when combined with difference
+pruning---exceeded our expectations for compression. It would be interesting to
+test whether this generalizes to a wider array of tasks, particularly since we
+only reap compression benefits as we leverage weight sharing over a number of
+tasks. Furthermore, from the distortions presented in \citet{lee2018deeptwist},
+we did not implement clustering-based quantization because of the significant
+computational bottleneck clustering with $k$-means on all of BERT's parameters
+posed. Future work could attempt to surmount this obstacle whether through
+increased computational resources or a more scalable clustering algorithm.
+
+Finally, we recognize our approaches are but a subset of the ways to go about
+compressing large language models such as BERT. Two alternatives stand out as
+particularly exciting possible future directions. \citet{liu2019multi} propose a
+method for complete weight sharing of BERT's encoder parameters across different
+tasks by simultaneously training for all tasks. We believe this approach could
+be relaxed through difference pruning to achieve a performance gain relative to
+each compression technique in isolation.
+
+% TODO: reverse of deeptwist -- what paper was this?
+
+\section*{Acknowledgements}
+
+% TODO: thank Rush + 287
 

### 2019-05-13 paper/paper.tex
Include mention of lottery ticket paper in conclusion

@@
 
-% TODO: reverse of deeptwist -- what paper was this?
+\citet{frankle2018lottery} articulate in their ``lottery ticket hypothesis''
+that most networks contain sparse sub-networks which can perform similarly well.
+They provide an algorithm for finding these ``lottery tickets'' whose main
+differences to DeepTwist are (1) that weights that get distorted to 0 are permanently
+masked and kept at 0, and (2) that the algorithm progressively increases the
+pruning rate. This framework could serve as a competitive alternative to
+DeepTwist, and it would be interesting to see how it performs with difference
+pruning.
 

### 2019-05-13 paper/paper.tex
Rewriting literature review and inserting matrix spectrum picture

@@
 
-DNNs have become extremely large in size with growing complexities. A BERT
-base model has 110M parameters and takes 438 MB disk space to store. This
+DNNs have become extremely large in size with growing complexities. A good
+example is BERT \citep{devlin2018bert}, which represents a growing
+literature in natural language processing in favor of pretraining 
+\citep{peters2018deep,radford2018improving,radford2019language}, which
+uses large models to learn from a large corpus of text in an unsupervised
+manner. The goal of such pretraining is creating contextualized
+representation of text in $\R^n$ which preserve certain structure of
+language. For different tasks, the researcher then \emph{fine-tunes} the
+pretrained model to the task, which may reach good performance since the
+pretrained representations are well-behaved representations of language
+strucutre. A downside of this framework is that each fine-tuned task
+requires a unique set of weights, which, when coupled with the raw size of
+these models, are cumbersome objects especially in a low hardware resource
+environment.
+
+The smaller \texttt{BERT-base-uncased} model has 110M parameters and takes
+438 MB disk space to store. This
 makes it very hard to deploy those models on mobile devices, which in most
@@
 The challenge that we are facing is therefore how to compress DNNs in size
-while keeping their predictive performance competitive with full model.
+while keeping their predictive performance competitive with full model. We are interested in compressing the language representation model BERT.  It is the state-of-art result in many natural
+language processing tasks  such as natural language inference, paraphrasing
+and named entity recognition.
 
@@
 
-We are interested in compressing the language representation model BERT
-\citep{devlin2018bert}.  It is the state-of-art result in many natural
-language processing tasks  such as natural language inference, paraphrasing
-and named entity recognition.
+There is a rich literature on compressing deep learning models, a selection
+of which we review in this section. For a comprehensive review, see  
+\citep{cheng2017survey}. The early work in compression is usually in a
+multi-stage framework, where model is trained, compressed, and then
+the compressed model is retrained for good performance.
 
-\citet{cheng2017survey} provides a comprehensive overview of the state-of-art
-methods to compress DNNs. Of the methods summarized by the paper, the ones
-that are of interest to our work are weight-pruning and quantization
-\citep{han2015deep}, and low-rank factorization \citep{denton2014exploiting}.
-Knowledge distillation, first proposed by \citep{bucilua2006model} as
-``knowledge transfer'', was recently popularized by
-\citep{hinton2015distilling}. It differs from the previously mentioned methods
-since it compresses an existing model by replacing it with a simpler model
-that is trained on its outputs.
+\citet{han2015deep} applies compression techniques to computer vision,
+where convolutional neural networks are popular and are often
+overparameterized \citep{yang2019fsnet},
+where the network is gradually \emph{pruned} and retrained in the first
+stage, where small
+weights are set
+to zero and gradient connections severed. In the second stage, the weights
+that survived pruning are clustered, and each cluster behaves like a single
+weight, with identical gradients. In the last stage, the model is Huffman
+encoded. Numerical experiments by \citet{han2015deep} show that the
+compression does not seem to influence performance. Moreover, the benefits
+of various compression techniques appear to stack without much loss in
+compression benefit. Moreover, convolutional network sizes are dominated by
+the convolution operations in
+lower layers \citep{denton2014exploiting}. \citet{denton2014exploiting}
+uses matrix factorization techniques on the matrices in convolutional
+layers, which has low effective rank.
 
-DeepTwist, a end-to-end training framework, allows us to incorporate
-compression procedures into training \citep{lee2018deeptwist}. Under this
+Pruning, quantization, and rank reduction are operations applied to a
+particular network's weights without altering the network architecture. 
+A different framework, knowledge distillation, first proposed by 
+\citep{bucilua2006model} as
+``knowledge transfer,'' was recently popularized by
+\citep{hinton2015distilling}. In knowledge distillation, a simple network,
+called the \emph{student network}, is not trained on the actual data but on
+the output of the large network one wishes to compress, called the 
+\emph{teacher network}. This procedure can even be extended by inserting
+various
+intermediate-sized networks between the teacher and student, intuitively
+termed
+\emph{teacher-assistant networks} \citep{mirzadeh2019improved}. We dicuss
+knowledge distillation in detail in \Cref{sec:training}.
+
+Compression techniques like pruning, quantization, and rank reduction can
+also be incorporated into an end-to-end framework, known as 
+\emph{DeepTwist}  \citep{lee2018deeptwist}, where training needs not be
+interrupted in some multi-stage process. Under this
 framework, the model parameters are occasionally distorted during training
@@
 % 6  &         diff prune &   $40$ &   $0.203$ &   $0.909$ \\
-% 7  &                svd &   $50$ &   $0.490$ &   $0.810$ \\
-% 8  &                svd &  $200$ &   $0.459$ &   $0.845$ \\
+% 7  &                rank reduction &   $50$ &   $0.490$ &   $0.810$ \\
+% 8  &                rank reduction &  $200$ &   $0.459$ &   $0.845$ \\
 % 9  &              prune &   $40$ &   $0.424$ &   $0.845$ \\
@@
 % 16 &         diff prune &   $60$ &   $0.209$ &   $0.920$ \\
-% 17 &                svd &  $100$ &   $0.515$ &   $0.823$ \\
-% 18 &                svd &  $150$ &   $0.456$ &   $0.828$ \\
+% 17 &                rank reduction &  $100$ &   $0.515$ &   $0.823$ \\
+% 18 &                rank reduction &  $150$ &   $0.456$ &   $0.828$ \\
 % 19 &         diff prune &   $80$ &   $2.533$ &   $0.491$ \\
@@
 Our non-difference distortions are more sensitive to the compression parameter
-(whether prune rate or SVD rank). We find it difficult to achieve performance
+(whether prune rate or rank reduction rank). We find it difficult to achieve performance
 comparable to the uncompressed BERT with a significantly compressed model. Among
 the different distortion methods, we favor pruning for its computational
-simplicity, and see no evidence that SVD achieves better compression.
+simplicity, and see no evidence that rank reduction achieves better compression.
+
+Remarkably, the fact that pruning and rank reduction incurs significant
+losses to the
+model seems to show that popular compression techniques that enjoy success
+in convolutional neural networks fail to generalize good performance to
+transformer-based language networks like BERT. We present some preliminary
+evidence in \Cref{fig:singular-values}, where we plot the singular values
+in one of the matrices in BERT. The effective rank of the matrix seems
+quite high, as the singular values are all sizable, decaying at a rate too
+slow for rank reduction techniques to be promising. This suggests that
+matrices in BERT are in fact effectively dense, unlike CNNs, where
+good compression relies on the effective sparsity of the matrices. 
+\begin{figure}[tb]
+    \centering
+    \includegraphics[width=0.5\textwidth]
+    {../figs/svd-singular-vals-distribution.png}
+    \caption{Distribution of singular values in one of BERT layers}
+    \label{fig:singular-values}
+\end{figure}
 

### 2019-05-13 paper/paper.tex
Acknowledgments
Fix second-half of edits

@@
   \]
-  be the vector where values in $\bvartheta$ below $t_p$ are zeroed.
+  is the vector where values in $\bvartheta$ below in absolute magnitude $t_p$
+  are zeroed.
 
@@
 
-% \subsection{Knowledge Distillation}
-
-% Example Structure:
-
-% \begin{itemize}
-% \item What is the formal definition of your problem?
-% \item What is the precise mathematical model you are using to represent it? In
-% almost all cases this will use the probabilistic language from class, e.g.
-%   \begin{equation}
-%   z \sim {\cal N}(0, \sigma^2)\label{eq:1}
-% \end{equation}
-% But it may also be a neural network, or a non-probabilistic loss,
-% \[ h_t \gets \mathrm{RNN}(x_{t}, h_{t-1} )\]
-
-% This is also a good place to reference a diagram such as Figure~\ref{fig:diagram}.
-
-% \item What are the parameters or latent variables of this model that you plan
-% on estimating or inferring? Be explicit. How many are there? Which are you
-% assuming are given? How do these relate to the original problem description?
-% \end{itemize}
-
-% \begin{figure}
-%   \centering
-%   \missingfigure[figheight=8cm]{}
-%   \caption{\label{fig:diagram} This is a good place to include a diagram
-%   showing how your model works. Examples include a graphical model or a neural
-%   network block diagram.}
-% \end{figure}
-
-% \subsection{Knowledge Distillation}
-
-% Example Structure:
-
-% \begin{itemize}
-% \item What is the formal definition of your problem?
-% \item What is the precise mathematical model you are using to represent it? In
-% almost all cases this will use the probabilistic language from class, e.g.
-%   \begin{equation}
-%   z \sim {\cal N}(0, \sigma^2)\label{eq:1}
-% \end{equation}
-% But it may also be a neural network, or a non-probabilistic loss,
-% \[ h_t \gets \mathrm{RNN}(x_{t}, h_{t-1} )\]
-
-% This is also a good place to reference a diagram such as Figure~\ref{fig:diagram}.
-
-% \item What are the parameters or latent variables of this model that you plan
-% on estimating or inferring? Be explicit. How many are there? Which are you
-% assuming are given? How do these relate to the original problem description?
-% \end{itemize}
-
-% \begin{figure}
-%   \centering
-%   \missingfigure[figheight=8cm]{}
-%   \caption{\label{fig:diagram} This is a good place to include a diagram
-%   showing how your model works. Examples include a graphical model or a neural
-%   network block diagram.}
-% \end{figure}
-
 \section{Methods}
@@
 
-\subsection{DeepTwist}
-We implement the DeepTwist framework with default frequency of distortion
-every 10 batches. Additionally, we ensure that training ends on a
-distortion step, so that the model produced by training has compression
-benefits. For $\prune$ and $\diffprune$ distortions, we use a single
-pruning rate held fixed throughout training.
-
 \subsection{Knowledge Distillation}
@@
 of \citet{kim2014convolutional} with kernel sizes $(3,4,5)$, hidden size
-$H=300$, no dropout, and $20$ kernels for each kernel size.\footnote{These are
-default in the implementation we used.}
+$H=300$, no dropout and 50\% dropout, and $20$ kernels for each kernel
+size.\footnote{These are default in the implementation we used.}
 
@@
 BERT.
+
+\subsection{DeepTwist}
+We implement the DeepTwist framework with default frequency of distortion
+every 10 batches. Additionally, we ensure that training ends on a
+distortion step, so that the model produced by training has compression
+benefits. For $\prune$ and $\diffprune$ distortions, we use a single
+pruning rate held fixed throughout training.
 
@@
 pruning, pruning, and rank reduction are implemented as \emph{distortion by
-layer} (see \Cref{sec:model}), where as ``difference pruning (global)''
+layer} (see \Cref{sec:model}), where as \emph{difference pruning (global)}
 indicates difference pruning, but pooling all parameter values from all layers.
@@
 \caption{Training loss (left), val. loss (middle), and val. accuracy
-(right) for LSTM KD}
+(right) plotted against number of batches of training for LSTM KD}
 \label{fig:kdlstmloss}
@@
 
-As expected, pruning a higher proportion of the weights decreases performance,
-but we are happily surprised at the relatively low magnitude of this effect even
-at high prune rates. Pruning with a global threshold rather than in a
-stratified way produces distinctly worse results. We suspect this is due to
-weights in different layers having different magnitudes, making a global
+As expected, difference pruning a higher proportion of the weights decreases
+performance, but we are happily surprised at the relatively low magnitude of
+this effect even at high prune rates. Pruning with a global threshold rather
+than in a stratified way produces distinctly worse results. We suspect this is
+due to weights in different layers having different magnitudes, making a global
 threshold have an undue effect on layers whose weights tend to be smaller. We
@@
 
+We thank Alexander M. Rush and the Harvard CS 287 community, without whom
+this work would not have been possible.
+
 % TODO: thank Rush + 287

### 2019-05-13 paper/paper.tex
Delete large comment blocks and TeX code cleanup
First half of paper proofread

@@
   We apply model compression techniques to fine-tuned BERT on multiclass
-  classification problems.  Knowledge distillation and DeepTwist-based compression techniques give
-  us moderate compression benefits for a commensurate decrease in model
-  performance. We achieve our most compelling results from employing the DeepTwist
-  framework to share weights across BERT models fine-tuned for different tasks. Our work demonstrates most weights need not change in the fine-tuning
-  process.
-%   \item This document describes the expected style, structure, and rough
+  classification problems.  Knowledge distillation and DeepTwist-based
+  compression techniques give us moderate compression benefits for a
+  commensurate decrease in model performance. We achieve our most compelling
+  results from employing the DeepTwist framework to share weights across
+  BERT-based
+  models fine-tuned for different tasks. Our work demonstrates most weights need
+  not change in the fine-tuning process.%   \item This document describes the expected style, structure, and rough
 %   proportions for your final project write-up.
@@
 
-% Example Structure:
-% \begin{itemize}
-% \item What is the problem of interest and what (high-level) are the current best methods for solving it?
-% \item How do you plan to improve/understand/modify this or related methods?
-% \item Preview your research process, list the contributions you made, and summarize your experimental findings.
-% \end{itemize}
-
 Deep Neural Networks (DNNs) have become the state-of-art for many tasks in
@@
 were applied by \citet{cheong2014transformer} on language models, Transformers
-in specific, and reduced the size by a factor of 5.85 while retaining 98.43\%
+especially, and reduced the size by a factor of 5.85 while retaining
+98.43\%
 of the performance. To the best of our knowledge, compressing language models
@@
 computer vision tasks, though the drop in performance is less negligible.
-Knowledge distillation also achieves the compression objective with more than
-desired decrease in predictive accuracy.
+Knowledge distillation also achieves the compression objective with more
+sacrifices in  predictive accuracy.
 
-We used two of the GLUE datasets SST-2 and QQP. We ran most of the experiments
+We use two of the GLUE datasets SST-2 and QQP. We conduct most of the
+experiments
 on SST-2, a binary sentiment classification task on single-sentence movie
-reviews. We validated the results on QQP, a binary classification task for
+reviews. We validate the results on QQP, a binary classification task for
 whether two questions asked on Quora are semantically equivalent.
 
-The most important contribution of this paper is that we proposed a new
-weight-sharing method called ``Difference Pruning'' which imposes constraint on
-the sparcity of weight difference with the pretrained BERT model. While
-uncompressed fine-tuned BERT model achieves 92.9\% validation accuracy on
-SST-2, the Difference Pruning model that keeps 99\% of the pretrained BERT
-weights achieves 91.3\% on the validation set. This enables multiple language
-modeling tasks to share the weights of pretrained BERT and each incurs minimal
-extra storage space requirements.
+Our most important contribution is a new weight-sharing method called
+\emph{difference pruning}, which imposes constraint on the sparsity of weight
+difference with the pretrained BERT model. While uncompressed fine-tuned BERT
+model achieves 92.9\% validation accuracy on SST-2, the difference pruning model
+that keeps 99\% of the pretrained BERT weights achieves 91.3\% on the validation
+set, which is on par with the fully fine-tuned model. This enables multiple
+language modeling tasks to share the weights of pretrained BERT, each incurring
+minimal extra storage space requirements.
 
@@
 
-% Example Structure:
-% \begin{itemize}
-% \item What information does a non-expert need to know about the problem domain?
-% \item What data exists for this problem?
-% \item What are the challenges/opportunities inherent to the data? (High
-% dimensional, sparse, missing data, noise, structure, discrete/continuous,
-% etc?)
-% \end{itemize}
-
 DNNs have become extremely large in size with growing complexities. A good
-example is BERT \citep{devlin2018bert}, which represents a growing
+example is BERT \citep{devlin2018bert}, which epitomizes a growing
 literature in natural language processing in favor of pretraining 
-\citep{peters2018deep,radford2018improving,radford2019language}, which
-uses large models to learn from a large corpus of text in an unsupervised
+\citep{peters2018deep,radford2018improving,radford2019language},
+using large models to learn from a large corpus of text in an unsupervised
 manner. The goal of such pretraining is creating contextualized
@@
 The smaller \texttt{BERT-base-uncased} model has 110M parameters and takes
-438 MB disk space to store. This
-makes it very hard to deploy those models on mobile devices, which in most
-cases have limited storage and RAM and low computational resources. As a
+438 MB of disk space to store. This
+makes it very hard to deploy these models on mobile devices, which in most
+cases have limited storage, RAM, and computational resources. As a
 result, we are not able to store multiple models for different tasks on mobile
@@
 
-% Example Structure:
-% \begin{itemize}
-% \item What 3-5 papers have been published in this space?
-% \item How do these  differ from your approach?
-% \item What data or methodologies do each of these works use?
-% \item How do you plan to compare to these methods?
-% \end{itemize}
-
 There is a rich literature on compressing deep learning models, a selection
@@
 
-\citet{han2015deep} applies compression techniques to computer vision,
-where convolutional neural networks are popular and are often
-overparameterized \citep{yang2019fsnet},
-where the network is gradually \emph{pruned} and retrained in the first
-stage, where small
-weights are set
-to zero and gradient connections severed. In the second stage, the weights
-that survived pruning are clustered, and each cluster behaves like a single
-weight, with identical gradients. In the last stage, the model is Huffman
-encoded. Numerical experiments by \citet{han2015deep} show that the
-compression does not seem to influence performance. Moreover, the benefits
-of various compression techniques appear to stack without much loss in
-compression benefit. Moreover, convolutional network sizes are dominated by
-the convolution operations in
-lower layers \citep{denton2014exploiting}. \citet{denton2014exploiting}
-uses matrix factorization techniques on the matrices in convolutional
-layers, which has low effective rank.
+\citet{han2015deep} applies compression techniques to computer vision, where
+convolutional neural networks are popular and are often overparameterized
+\citep{yang2019fsnet}, where the network is gradually \emph{pruned} and
+retrained in the first stage, by setting small weights to zero and severing
+gradient connections. In the second stage, the weights that survived pruning are
+clustered, and each cluster behaves like a single weight, with identical
+gradients. In the last stage, the model is Huffman encoded. Numerical
+experiments by \citet{han2015deep} show that the compression does not seem to
+influence performance. Moreover, the benefits of various compression techniques
+appear to stack without much loss in compression benefit. Additionally,
+convolutional network sizes are dominated by the convolution operations in lower
+layers \citep{denton2014exploiting}. \citet{denton2014exploiting} uses matrix
+factorization techniques on the matrices in convolutional layers, which has low
+effective rank.
 
@@
 
+\section{Model}
+\label{sec:model}
+
+We first set up some notation. Let $F_\btheta = G_\bpsi \circ \bert_\bphi$ be
+a fine-tuned model where $\btheta = (\bphi, \bpsi)$ are parameters of the
+subparts of the model. $\bert_\bphi$ is a BERT model where the pretrained
+weights are $\bphi_0 = (\bphi_0^i)_{i=1}^n$, and $G_\bpsi$ is additional
+layers for fine-tuning BERT, parameterized by $\bpsi$. We decompose the
+subparts of the model into layers: \begin{align*}
+\bert_\bphi &= f_{n}^{\bphi_n} \circ \cdots \circ f_1^{\bphi_1} \\
+G_\bpsi &= g_{m}^{\bpsi_m} \circ \cdots \circ g_1^{\bpsi_1}.
+\end{align*}
+
+% \subsection{DeepTwist-based Weight Distortions}
+
+Given training data $(\bm x_i, y_i)_{i=1}^N$, where $\bm x_i$ are one-hot
+encoded tokens, we train by solving the standard maximum likelihood problem
+where the objective is \[
+\min_{\btheta} \sum_{i=1}^N \ell\pr{F_\btheta(\bm x_i), y_i}
+\]
+for some loss function specific to the task. For instance, $\ell$ is
+cross-entropy loss for a (multiclass) classification problem, and $\ell$ is
+mean-squared-error for a regression problem, which correspond to
+log-likelihoods in Categorical and Gaussian models, respectively.
+
 \section{Inference (or Training)}
@@
 In this paper, we limit our purview to text classification tasks. Training
-neural-network-based systems for this task typically consists of a form of
-gradient descent based on a differentiable loss function which takes in the
-prediction for a given example and the correct label. That is, if we have
+neural-network-based systems for this task typically consists of
+gradient-descent-based optimizers applied to a differentiable loss
+function, which takes in the prediction for a given example and the correct label. That is, if we have
 training data $(\bm{x}_i, y_i)$ and model $f$, we would aim to minimize,
 \[ \ell(f(\bm{x_i}), y_i)\]
-where usually the loss function is taken to be Cross-Entropy loss. When we
+where usually the loss function is taken to be cross-entropy loss. When we
 already have a model $f$ that performs well, we can leverage this training
@@
 \[ \ell(g(\bm{x_i}), f(\bm{x_i})).\]
-Here, we can no longer use Cross-Entropy loss because $f(\bm{x}_i)$ is a
-probability distribution rather than a specific label. However, we can take
+We can take
 $\ell$ to be either mean-square error (MSE) between the probabilities in
@@
 An additional benefit from knowledge distillation arises from BERT's
-pre-training. Because BERT is pretrained on large amounts of unstructured
+pretraining. Because BERT is pretrained on large amounts of unstructured
 data, it contains a powerful language model which likely would be impossible
-to learn from the specific task's data-set. To an extent, relevant features
+to learn from the specific task's dataset. To an extent, relevant features
 from this language model are what make BERT so powerful once it's fine-tuned.
@@
 To provide a concrete example of how this might work, suppose BERT captures
-from its pre-training that ``bad'', ``horrible,'' and ``terrible'' are
+from its pretraining that ``bad'', ``horrible,'' and ``terrible'' are
 approximate synonyms. In a sentiment task, these three words appear in three
@@
 \emph{DeepTwist}, whose training loop is characterized by \cref{algo:deeptwist}.
-Training of the model closely resembles SGD with one important modification:
-every $S_d$ batches, the model weights are transformed by a \emph{distortion}
-function.
+Training of the model closely resembles normal gradient training with one
+important modification: every $S_d$ batches, the model weights are transformed
+by a \emph{distortion} function.
 
@@
     \STATE{$n \leftarrow$ number of batches per epoch}
-    \STATE{$\theta \leftarrow$ initialization of model parameters}
+    \STATE{$\btheta \leftarrow$ initialization of model parameters}
     \STATE{$k \leftarrow$ number of epochs to train}
@@
       \STATE{batch $\leftarrow$ batches[$i \pmod n$]}
-      \STATE{$\theta \leftarrow \theta - \eta \nabla \ell(\theta,
+      \STATE{$\btheta \leftarrow \btheta - \eta \nabla \ell(\btheta,
       \text{batch})$}
@@
       \IF{$i \equiv 0 \pmod{S_d}$}
-        \STATE{$\theta \leftarrow \distortion(\theta)$}
+        \STATE{$\btheta \leftarrow \distortion(\btheta)$}
       \ENDIF
     \ENDFOR
-    \STATE{$\theta \leftarrow \distortion(\theta)$}
+    \STATE{$\btheta \leftarrow \distortion(\btheta)$}
   \end{algorithmic}
@@
 distortion function should have a parameterization that takes less space in
-memory than then range of all possible $\theta$s. For example, if $\theta \in
+memory than then range of all possible $\btheta$s. For example, if $\btheta \in
 \mathbb{R}^{m,n}$, and the distortion produces a matrix of rank 1, then any
-distorted matrix could be uniquely identified by $\theta' \in \mathbb{R}^{n+m}$
+distorted matrix could be uniquely identified by $\btheta' \in \mathbb{R}^{n+m}$
 through a matrix factorization.
 
-It is important to note that while $\theta$ will be compressible immediately
+It is important to note that while $\btheta$ will be compressible immediately
 after a distortion step, there is no guarantee that it will remain so after some
@@
 
-\section{Model}
-\label{sec:model}
-
-We first set up some notation. Let $F_\btheta = G_\bpsi \circ \bert_\bphi$ be
-a transformed model where $\btheta = (\bphi, \bpsi)$ be parameters of the
-subparts of the model. $\bert_\bphi$ is a BERT model where the pretrained
-weights are $\bphi_0 = (\bphi_0^i)_{i=1}^n$, and $G_\bpsi$ is additional
-layers for fine-tuning BERT, parameterized by $\bpsi$. We decompose the
-subparts of the model into layers: \begin{align*}
-\bert_\bphi &= f_{n}^{\bphi_n} \circ \cdots \circ f_1^{\bphi_1} \\
-G_\bpsi &= g_{m}^{\bpsi_m} \circ \cdots \circ g_1^{\bpsi_1}.
-\end{align*}
-
-% \subsection{DeepTwist-based Weight Distortions}
-
-Given training data $(\bm x_i, y_i)_{i=1}^N$, where $\bm x_i$ are one-hot
-encoded tokens, we train by solving the standard maximum likelihood problem
-where \[
-\min_{\btheta} \sum_{i=1}^N \ell\pr{y_i, F_\btheta(\bm x_i)}
-\]
-for some loss function specific to the task. For instance, $\ell$ is
-cross-entropy loss for a (multiclass) classification problem, and $\ell$ is
-mean-squared-error for a regression problem, which correspond to
-log-likelihoods in Categorical and Gaussian models, respectively. The
-innovation of DeepTwist-based training is perturbing the usual gradient-based
-optimization by repeatedly distorting the current weights to achieve
-compression objectives.
-
-Specifically, the DeepTwist framework presented in \Cref{sec:training} applies
-a distortion step for fixed intervals during training, where \[
+\section{Distortions}
+\label{sec:distortions}
+The innovation of DeepTwist-based training is perturbing the usual
+gradient-based optimization by repeatedly distorting the current weights to
+achieve compression objectives. Specifically, the DeepTwist framework presented
+in \Cref{sec:training} applies a distortion step for fixed intervals during
+training, where \[
 \btheta \gets \distortion(\btheta). 
@@
 
-% \begin{itemize}
-% \item What were the results comparing previous work / baseline systems / your
-% systems on the main task?
-% \item What were the secondary results comparing the variants of your system?
-% \item This section should be fact based and relatively dry. What happened,
-% what was significant?
-% \end{itemize}
-
-% \begin{table*}
-%   \centering
-%   \missingfigure{}
-%   \caption{This is usually a table. Tables with numbers are generally easier
-%   to read than graphs, so prefer when possible.}
-%   \label{fig:mainres}
-% \end{table*}
-
-% \begin{table}[tbh]
-%         \caption{Results for DeepTwist}
-%         \label{tab:deeptwist_results}
-%         \centering
-%         \vspace{1em}
-%         \begin{tabular}{lccccc}
-% \toprule
-% {} &               type &  param &  val loss &   val acc \\
-% {} & 
-% \hypertarget{tabcol:1}{(1)} & \hypertarget{tabcol:2}{(2)} & \hypertarget{tabcol:3}{(3)} & \hypertarget{tabcol:4}{(4)} \\ \midrule
-% 0  &  diff prune global &   $90$ &   $0.211$ &   $0.912$ \\
-% 1  &              prune &   $20$ &   $0.291$ &   $0.886$ \\
-% 2  &              prune &   $80$ &   $0.532$ &   $0.767$ \\
-% 3  &         diff prune &   $80$ &   $0.222$ &   $0.916$ \\
-% 4  &  diff prune global &   $99$ &       --- &       --- \\
-% 5  &  diff prune global &   $90$ &   $0.213$ &   $0.916$ \\
-% 6  &         diff prune &   $40$ &   $0.203$ &   $0.909$ \\
-% 7  &                rank reduction &   $50$ &   $0.490$ &   $0.810$ \\
-% 8  &                rank reduction &  $200$ &   $0.459$ &   $0.845$ \\
-% 9  &              prune &   $40$ &   $0.424$ &   $0.845$ \\
-% 10 &              prune &   $60$ &   $0.425$ &   $0.815$ \\
-% 11 &  diff prune global &   $99$ &   $0.230$ &   $0.901$ \\
-% 12 &  diff prune global &   $99$ &   $0.222$ &   $0.905$ \\
-% 13 &         diff prune &   $99$ &   $0.222$ &   $0.913$ \\
-% 14 &         diff prune &   $95$ &   $0.221$ &   $0.916$ \\
-% 15 &         diff prune &   $90$ &   $0.216$ &   $0.916$ \\
-% 16 &         diff prune &   $60$ &   $0.209$ &   $0.920$ \\
-% 17 &                rank reduction &  $100$ &   $0.515$ &   $0.823$ \\
-% 18 &                rank reduction &  $150$ &   $0.456$ &   $0.828$ \\
-% 19 &         diff prune &   $80$ &   $2.533$ &   $0.491$ \\
-% 20 &         diff prune &   $90$ &       --- &       --- \\
-% 21 &  diff prune global &    $0$ &   $0.738$ &   $0.509$ \\
-% 22 &         diff prune &    $0$ &   $0.692$ &   $0.522$ \\
-% 23 &         diff prune &    $0$ &   $1.854$ &   $0.491$ \\
-% \bottomrule
-% \end{tabular}
-
-% \end{table}
-
 \input{../tabs/hierarchical_deeptwist_table.tex}
@@
 \input{../tabs/kd_table.tex}
-
-% \begin{table}[tbh]
-%         \caption{Results for Knowledge Distillation}
-%         \label{tab:kd_results}
-%         \centering
-%         \vspace{1em}
-%         \begin{tabular}{lccccccc}
-% \toprule
-% {} &  framework &  type &  val loss &  ß val acc \\
-% {} & \hypertarget{tabcol:1}{(1)} & \hypertarget{tabcol:2}{(2)} & \hypertarget{tabcol:3}{(3)} & \hypertarget{tabcol:4}{(4)} \\
-% \midrule
-% 0 &        nokd &   CNN &   $0.906$ &   $0.799$ \\
-% 1 &        nokd &   CNN &   $0.448$ &   $0.784$ \\
-% 2 &        nokd &   CNN &   $0.856$ &   $0.812$ \\
-% 3 &          kd &  LSTM &   $0.738$ &   $0.831$ \\
-% 4 &          kd &   CNN &   $0.423$ &   $0.834$ \\
-% \bottomrule
-% \end{tabular}
-% \label{tbl:kdresults}
-% \end{table}
 
@@
 
-% Things to say about DeepTwist
-% \begin{itemize}
-%   \item Stratified prune better
-%   \item Prune rate mad robust
-%   \item Diff gud
-%   \item ``Improved performance''
-%   \item QQP takes long, but looks okay
-%   \item Didn't try only pruning the $\bert$ part
-% \end{itemize}
-% 
-% Things to say about KD
-% \begin{itemize}
-%   \item it bad
-%   \item doesn't work
-%   \item LSTM weird/CNN incredibly noisy
-%   \item \TODO{compare}
-% \end{itemize}
-
 When compared to the performance of a fine-tuned BERT on SST-2, our Knowledge
@@
 epochs to grow to a point where it can meaningfully update parameters.
-
-% \begin{itemize}
-% \item What conclusions can you draw from the results section?
-% \item Is there further analysis you can do into the results of the system? Here
-% is a good place to include visualizations, graphs, qualitative analysis of your
-% results.
-% 
-% \item  What questions remain open? What did you think might work, but did not?
-% \end{itemize}
-
-% \begin{figure}
-%   \centering
-%   \missingfigure{}
-%   \missingfigure{}
-%   \missingfigure{}
-%   \caption{Visualizations of the internals of the system.}
-% \end{figure}
 
@@
 They provide an algorithm for finding these ``lottery tickets'' whose main
-differences to DeepTwist are (1) that weights that get distorted to 0 are permanently
-masked and kept at 0, and (2) that the algorithm progressively increases the
-pruning rate. This framework could serve as a competitive alternative to
-DeepTwist, and it would be interesting to see how it performs with difference
-pruning.
+differences to DeepTwist are (1) that weights that get distorted to 0 are
+permanently masked and kept at 0, and (2) that the algorithm progressively
+increases the pruning rate. This framework could serve as a competitive
+alternative to DeepTwist, and it would be interesting to see how it performs
+with difference pruning.
 
@@
 
-% TODO: thank Rush + 287
-
-% \textbf{Do not} include acknowledgements in the initial version of
-% the paper submitted for blind review.
-
-% If a paper is accepted, the final camera-ready version can (and
-% probably should) include acknowledgements. In this case, please
-% place such acknowledgements in an unnumbered section at the
-% end of the paper. Typically, this will include thanks to reviewers
-% who gave useful comments, to colleagues who contributed to the ideas,
-% and to funding agencies and corporate sponsors that provided financial
-% support.
-
 \bibliography{paper}

### 2019-05-13 paper/paper.tex
Adding code repository link

@@
 language modeling tasks to share the weights of pretrained BERT, each incurring
-minimal extra storage space requirements.
+minimal extra storage space requirements.\footnote{Code available at \url{https://github.com/frtennis1/cs287-project}}
 
@@
 
-The challenge that we are facing is therefore how to compress DNNs in size
-while keeping their predictive performance competitive with full model. We are interested in compressing the language representation model BERT.  It is the state-of-art result in many natural
+We are interested in compressing the language representation model BERT.  It is the state-of-art result in many natural
 language processing tasks  such as natural language inference, paraphrasing

### 2019-05-13 paper/paper.tex
Minor paper fix

--- 2019-05-13 paper/paper.tex
@@
 \begin{abstract}
-% \raggedright
-  We apply model compression techniques to fine-tuned BERT on multiclass
-  classification problems.  Knowledge distillation and DeepTwist-based compression techniques give
+\raggedright
+  \begin{itemize}
+  \item We apply model compression techniques to fine-tuned BERT on multiclass
+  classification problems.
+  \item Knowledge distillation and DeepTwist-based compression techniques give
   us moderate compression benefits for a commensurate decrease in model
-  performance. We achieve our most compelling results from employing the DeepTwist
-  framework to share weights across BERT models fine-tuned for different tasks. Our work demonstrates most weights need not change in the fine-tuning
+  performance.
+  \item We achieve our most compelling results from employing the DeepTwist
+  framework to share weights across BERT models fine-tuned for different tasks.
+  \item Our work demonstrates most weights need not change in the fine-tuning
   process.
@@
 %   main contributions of the work in the length given.
-  % \end{itemize}
+  \end{itemize}
 
@@
 
-Deep Neural Networks (DNNs) have become the state-of-art for many tasks in
+Deep Neural Networks (DDNs) have become the state-of-art for many tasks in
 language modeling. At the same time, they have become progressively larger in
-size, due to both larger out-of-box pretrained embeddings and deeper
+size, due to both larger out-of-box pre-trained embeddings and deeper
 networks. However, in order to deploy the models on more resource-constrained
@@
 computer vision tasks, though the drop in performance is less negligible.
-Knowledge distillation also achieves the compression objective with more than
+Knowledge Distillation also achieves the compression objective with more than
 desired decrease in predictive accuracy.
@@
 weight-sharing method called ``Difference Pruning'' which imposes constraint on
-the sparcity of weight difference with the pretrained BERT model. While
+the sparcity of weight difference with the pre-trained BERT model. While
 uncompressed fine-tuned BERT model achieves 92.9\% validation accuracy on
-SST-2, the Difference Pruning model that keeps 99\% of the pretrained BERT
+SST-2, the Difference Pruning model that keeps 99\% of the pre-trained BERT
 weights achieves 91.3\% on the validation set. This enables multiple language
-modeling tasks to share the weights of pretrained BERT and each incurs minimal
+modeling tasks to share the weights of pre-trained BERT and each incurs minimal
 extra storage space requirements.
@@
 
-DNNs have become extremely large in size with growing complexities. A good
-example is BERT \citep{devlin2018bert}, which represents a growing
-literature in natural language processing in favor of pretraining 
-\citep{peters2018deep,radford2018improving,radford2019language}, which
-uses large models to learn from a large corpus of text in an unsupervised
-manner. The goal of such pretraining is creating contextualized
-representation of text in $\R^n$ which preserve certain structure of
-language. For different tasks, the researcher then \emph{fine-tunes} the
-pretrained model to the task, which may reach good performance since the
-pretrained representations are well-behaved representations of language
-strucutre. A downside of this framework is that each fine-tuned task
-requires a unique set of weights, which, when coupled with the raw size of
-these models, are cumbersome objects especially in a low hardware resource
-environment.
-
-The smaller \texttt{BERT-base-uncased} model has 110M parameters and takes
-438 MB disk space to store. This
+DNNs have become extremely large in size with growing complexities. A BERT
+base model has 110M parameters and takes 438 MB disk space to store. This
 makes it very hard to deploy those models on mobile devices, which in most
@@
 The challenge that we are facing is therefore how to compress DNNs in size
-while keeping their predictive performance competitive with full model. We are interested in compressing the language representation model BERT.  It is the state-of-art result in many natural
-language processing tasks  such as natural language inference, paraphrasing
-and named entity recognition.
+while keeping their predictive performance competitive with full model.
 
@@
 
-There is a rich literature on compressing deep learning models, a selection
-of which we review in this section. For a comprehensive review, see  
-\citep{cheng2017survey}. The early work in compression is usually in a
-multi-stage framework, where model is trained, compressed, and then
-the compressed model is retrained for good performance.
+We are interested in compressing the language representation model BERT
+\citep{devlin2018bert}.  It is the state-of-art result in many natural
+language processing tasks  such as natural language inference, paraphrasing
+and named entity recognition.
 
-\citet{han2015deep} applies compression techniques to computer vision,
-where convolutional neural networks are popular and are often
-overparameterized \citep{yang2019fsnet},
-where the network is gradually \emph{pruned} and retrained in the first
-stage, where small
-weights are set
-to zero and gradient connections severed. In the second stage, the weights
-that survived pruning are clustered, and each cluster behaves like a single
-weight, with identical gradients. In the last stage, the model is Huffman
-encoded. Numerical experiments by \citet{han2015deep} show that the
-compression does not seem to influence performance. Moreover, the benefits
-of various compression techniques appear to stack without much loss in
-compression benefit. Moreover, convolutional network sizes are dominated by
-the convolution operations in
-lower layers \citep{denton2014exploiting}. \citet{denton2014exploiting}
-uses matrix factorization techniques on the matrices in convolutional
-layers, which has low effective rank.
+\citet{cheng2017survey} provides a comprehensive overview of the state-of-art
+methods to compress DNNs. Of the methods summarized by the paper, the ones
+that are of interest to our work are weight-pruning and quantization
+\citep{han2015deep}, and low-rank factorization \citep{denton2014exploiting}.
+Knowledge distillation, first proposed by \citep{bucilua2006model} as
+``knowledge transfer'', was recently popularized by
+\citep{hinton2015distilling}. It differs from the previously mentioned methods
+since it compresses an existing model by replacing it with a simpler model
+that is trained on its outputs.
 
-Pruning, quantization, and rank reduction are operations applied to a
-particular network's weights without altering the network architecture. 
-A different framework, knowledge distillation, first proposed by 
-\citep{bucilua2006model} as
-``knowledge transfer,'' was recently popularized by
-\citep{hinton2015distilling}. In knowledge distillation, a simple network,
-called the \emph{student network}, is not trained on the actual data but on
-the output of the large network one wishes to compress, called the 
-\emph{teacher network}. This procedure can even be extended by inserting
-various
-intermediate-sized networks between the teacher and student, intuitively
-termed
-\emph{teacher-assistant networks} \citep{mirzadeh2019improved}. We dicuss
-knowledge distillation in detail in \Cref{sec:training}.
-
-Compression techniques like pruning, quantization, and rank reduction can
-also be incorporated into an end-to-end framework, known as 
-\emph{DeepTwist}  \citep{lee2018deeptwist}, where training needs not be
-interrupted in some multi-stage process. Under this
+DeepTwist, a end-to-end training framework, allows us to incorporate
+compression procedures into training \citep{lee2018deeptwist}. Under this
 framework, the model parameters are occasionally distorted during training
@@
 An additional benefit from knowledge distillation arises from BERT's
-pre-training. Because BERT is pretrained on large amounts of unstructured
+pre-training. Because BERT is pre-trained on large amounts of unstructured
 data, it contains a powerful language model which likely would be impossible
@@
 
-\subsection{DeepTwist}
+\subsection{Deep Twist}
 
@@
   \]
-  is the vector where values in $\bvartheta$ below in absolute magnitude $t_p$
-  are zeroed.
+  be the vector where values in $\bvartheta$ below $t_p$ are zeroed.
 
@@
   as a price of the generality, pruning fails to be tailored to the nature of
-  BERT being a pretrained model. Suppose the pretrained weights $\bphi_0 $
+  BERT being a pre-trained model. Suppose the pretrained weights $\bphi_0 $
   capture certain structure of language, then dramatic distortions to
@@
 a compression rate of \[
-\rho = 1-\frac{r(n+m)}{2mn}.
+\rho = \frac{r(n+m)}{2mn}.
 \]
@@
 $\tilde U \tilde \Sigma \tilde V$.
+
+% \subsection{Knowledge Distillation}
+
+% Example Structure:
+
+% \begin{itemize}
+% \item What is the formal definition of your problem?
+% \item What is the precise mathematical model you are using to represent it? In
+% almost all cases this will use the probabilistic language from class, e.g.
+%   \begin{equation}
+%   z \sim {\cal N}(0, \sigma^2)\label{eq:1}
+% \end{equation}
+% But it may also be a neural network, or a non-probabilistic loss,
+% \[ h_t \gets \mathrm{RNN}(x_{t}, h_{t-1} )\]
+
+% This is also a good place to reference a diagram such as Figure~\ref{fig:diagram}.
+
+% \item What are the parameters or latent variables of this model that you plan
+% on estimating or inferring? Be explicit. How many are there? Which are you
+% assuming are given? How do these relate to the original problem description?
+% \end{itemize}
+
+% \begin{figure}
+%   \centering
+%   \missingfigure[figheight=8cm]{}
+%   \caption{\label{fig:diagram} This is a good place to include a diagram
+%   showing how your model works. Examples include a graphical model or a neural
+%   network block diagram.}
+% \end{figure}
+
+% \subsection{Knowledge Distillation}
+
+% Example Structure:
+
+% \begin{itemize}
+% \item What is the formal definition of your problem?
+% \item What is the precise mathematical model you are using to represent it? In
+% almost all cases this will use the probabilistic language from class, e.g.
+%   \begin{equation}
+%   z \sim {\cal N}(0, \sigma^2)\label{eq:1}
+% \end{equation}
+% But it may also be a neural network, or a non-probabilistic loss,
+% \[ h_t \gets \mathrm{RNN}(x_{t}, h_{t-1} )\]
+
+% This is also a good place to reference a diagram such as Figure~\ref{fig:diagram}.
+
+% \item What are the parameters or latent variables of this model that you plan
+% on estimating or inferring? Be explicit. How many are there? Which are you
+% assuming are given? How do these relate to the original problem description?
+% \end{itemize}
+
+% \begin{figure}
+%   \centering
+%   \missingfigure[figheight=8cm]{}
+%   \caption{\label{fig:diagram} This is a good place to include a diagram
+%   showing how your model works. Examples include a graphical model or a neural
+%   network block diagram.}
+% \end{figure}
 
@@
 early stopping in training, with patience of 1 epoch, and early stopping is
-guided by validation loss.
+guided by validation error.
+
+\subsection{DeepTwist}
+We implement the DeepTwist framework with default frequency of distortion
+every 10 batches. Additionally, we ensure that training ends on a
+distortion step, so that the model produced by training has compression
+benefits. For $\prune$ and $\diffprune$ distortions, we use a single
+pruning rate held fixed throughout training.
 
@@
 of \citet{kim2014convolutional} with kernel sizes $(3,4,5)$, hidden size
-$H=300$, no dropout and 50\% dropout, and $20$ kernels for each kernel
-size.\footnote{These are default in the implementation we used.}
+$H=300$, no dropout, and $20$ kernels for each kernel size.\footnote{These are
+default in the implementation we used.}
 
@@
 
-\subsection{DeepTwist}
-We implement the DeepTwist framework with default frequency of distortion
-every 10 batches. Additionally, we ensure that training ends on a
-distortion step, so that the model produced by training has compression
-benefits. For $\prune$ and $\diffprune$ distortions, we use a single
-pruning rate held fixed throughout training.
-
 \section{Results}
 
-We show our results in \Cref {tab:deeptwist_results,tab:kd_results}. In the top
-pane of \Cref {tab:deeptwist_results}, we show the result of various
-DeepTwist-based compression techniques on the sentiment classification task,
-SST-2, stratifying by method and then by parameter of the method. Difference
-pruning, pruning, and rank reduction are implemented as \emph{distortion by
-layer} (see \Cref{sec:model}), where as \emph{difference pruning (global)}
-indicates difference pruning, but pooling all parameter values from all layers.
-The bottom pane of \Cref{tab:deeptwist_results} shows the performance on QQP of
-some competitive-performing model setups on SST-2, which are all
-difference-pruning based. In \Cref{tab:kd_results}, we present some knowledge
-distillation experiments, with the student network being an LSTM or a CNN, with
-or without dropout \citep{kim2014convolutional}.
-
-Pruning admits a simple upper bound for compression, which is simply the
-pruning ratio.\footnote{The exact compression rate is complicated, due to
-the sparse data structure implemented for the compressed model} Compression
-rate for difference pruning depends on the number of tasks the user
-desires to perform, since difference pruning is understood to be a form of
-weight sharing. In that context, the (upper bound) compression rate of
-difference
-pruning
-is also self-evident. The compression rate achieved by rank reduction is \[
-\rho = 1 - \frac{r(n+m)}{2mn}.
-\]
-Since most matrices in \texttt{BERT-base-uncased} is $768\times 768,$ the
-compression rate is approximately \[
-\rho \approx 1 - \frac{r}{768} = (74.0\%,
-80.5\%,
-87.0\%,
-93.5\%)
-\]
-for $r = (200,150,100,50)$, respectively.
-
-For the most part, difference pruning seems to be robust to the pruning
-rate. As a sanity check, we include difference pruning with 100\% pruning
-rate, which is equivalent to BERT model without fine-tuning, and obtaining
-essentially uniform results on the validation set. Difference pruning also
-seems to outperform both ``first-order'' DeepTwist techniques, pruning and
-rank reduction, which is unsurprising as difference pruning uses more
-parameters and uses parameters that are pretrained. Difference pruning also
-seems to extend to other tasks in GLUE, as it retains its behavior in
-SST-2 to QQP, for the most part. Knowledge distillation seems less
-promising. While knowledge distillation
-slightly improves upon the model directly trained on data, it does not
-fully replicate the performance of the teacher network. We now discuss our
-results in detail.
-
-% \begin{itemize}
-% \item What were the results comparing previous work / baseline systems / your
-% systems on the main task?
-% \item What were the secondary results comparing the variants of your system?
-% \item This section should be fact based and relatively dry. What happened,
-% what was significant?
-% \end{itemize}
+\begin{itemize}
+\item What were the results comparing previous work / baseline systems / your
+systems on the main task?
+\item What were the secondary results comparing the variants of your system?
+\item This section should be fact based and relatively dry. What happened, what
+was significant?
+\end{itemize}
 
@@
 % 6  &         diff prune &   $40$ &   $0.203$ &   $0.909$ \\
-% 7  &                rank reduction &   $50$ &   $0.490$ &   $0.810$ \\
-% 8  &                rank reduction &  $200$ &   $0.459$ &   $0.845$ \\
+% 7  &                svd &   $50$ &   $0.490$ &   $0.810$ \\
+% 8  &                svd &  $200$ &   $0.459$ &   $0.845$ \\
 % 9  &              prune &   $40$ &   $0.424$ &   $0.845$ \\
@@
 % 16 &         diff prune &   $60$ &   $0.209$ &   $0.920$ \\
-% 17 &                rank reduction &  $100$ &   $0.515$ &   $0.823$ \\
-% 18 &                rank reduction &  $150$ &   $0.456$ &   $0.828$ \\
+% 17 &                svd &  $100$ &   $0.515$ &   $0.823$ \\
+% 18 &                svd &  $150$ &   $0.456$ &   $0.828$ \\
 % 19 &         diff prune &   $80$ &   $2.533$ &   $0.491$ \\
@@
 
-\begin{figure*}[htb]
-\centering
-\includegraphics[width=\textwidth]{../figs/kd_lstm_training.png}
-\caption{Training loss (left), val. loss (middle), and val. accuracy
-(right) plotted against number of batches of training for LSTM KD}
-\label{fig:kdlstmloss}
-\end{figure*}
-
 Our most striking result is the robust performance of difference pruning. Even
@@
 SST-2, but we see success with this method on QQP as well, suggesting that
-small changes to pretrained BERT are sufficient for performance on a specific
+small changes to pre-trained BERT are sufficient for performance on a specific
 task.
 
-As expected, difference pruning a higher proportion of the weights decreases
-performance, but we are happily surprised at the relatively low magnitude of
-this effect even at high prune rates. Pruning with a global threshold rather
-than in a stratified way produces distinctly worse results. We suspect this is
-due to weights in different layers having different magnitudes, making a global
+As expected, pruning a higher proportion of the weights decreases performance,
+but we are happily surprised at the relatively low magnitude of this effect even
+at high prune rates. Pruning with a global threshold rather than in a
+stratified way produces distinctly worse results. We suspect this is due to
+weights in different layers having different magnitudes, making a global
 threshold have an undue effect on layers whose weights tend to be smaller. We
@@
 Our non-difference distortions are more sensitive to the compression parameter
-(whether prune rate or rank reduction rank). We find it difficult to achieve performance
+(whether prune rate or SVD rank). We find it difficult to achieve performance
 comparable to the uncompressed BERT with a significantly compressed model. Among
 the different distortion methods, we favor pruning for its computational
-simplicity, and see no evidence that rank reduction achieves better compression.
-
-Remarkably, the fact that pruning and rank reduction incurs significant
-losses to the
-model seems to show that popular compression techniques that enjoy success
-in convolutional neural networks fail to generalize good performance to
-transformer-based language networks like BERT. We present some preliminary
-evidence in \Cref{fig:singular-values}, where we plot the singular values
-in one of the matrices in BERT. The effective rank of the matrix seems
-quite high, as the singular values are all sizable, decaying at a rate too
-slow for rank reduction techniques to be promising. This suggests that
-matrices in BERT are in fact effectively dense, unlike CNNs, where
-good compression relies on the effective sparsity of the matrices. 
-\begin{figure}[tb]
-    \centering
-    \includegraphics[width=0.5\textwidth]
-    {../figs/svd-singular-vals-distribution.png}
-    \caption{Distribution of singular values in one of BERT layers}
-    \label{fig:singular-values}
-\end{figure}
+simplicity, and see no evidence that SVD achieves better compression.
 
@@
 
+\begin{figure*}[tb]
+\centering
+\includegraphics[width=\textwidth]{../figs/kd_lstm_training.png}
+\caption{Training loss (left), val. loss (middle), and val. accuracy
+(right) for LSTM KD}
+\label{fig:kdlstmloss}
+\end{figure*}
+
 % \begin{itemize}
@@
 
-Knowledge Distillation displayed promise by improving student networks'
-performance versus training only on the classes $y_i$. However, the student
-networks fell short of replicating uncompressed BERT's performance. It is
-possible that future variations on our work could achieve competitive
-compression. In particular, we restrict our knowledge distillation only to the
-samples in the original training set. However, there is no need to perform
-training so narrowly since the teacher network can annotate any unsupervised
-data. It is likely that doing so would further increase performance, though we
-can only speculate as to the magnitude of the benefit.
+\begin{itemize}
+\item What happened?
+\item What next?
+\end{itemize}
 
-It is also possible that our choice of student network colored our results. We
-aimed for architectures known to work on SST-2 while being much smaller, such as
-\citet{kim2014convolutional}'s CNN. It is possible that we aimed too small and
-would be better served by a more complex model---possibly even a smaller version
-of BERT. Finally, in all our experiments our teacher network is a single
-fine-tuned version of BERT. Since teacher network complexity doesn't contribute
-to the complexity of the final model, we could instead use an ensemble of BERTs
-(or even other models) as our teacher network.
-
-The DeepTwist framework---particularly when combined with difference
-pruning---exceeded our expectations for compression. It would be interesting to
-test whether this generalizes to a wider array of tasks, particularly since we
-only reap compression benefits as we leverage weight sharing over a number of
-tasks. Furthermore, from the distortions presented in \citet{lee2018deeptwist},
-we did not implement clustering-based quantization because of the significant
-computational bottleneck clustering with $k$-means on all of BERT's parameters
-posed. Future work could attempt to surmount this obstacle whether through
-increased computational resources or a more scalable clustering algorithm.
-
-Finally, we recognize our approaches are but a subset of the ways to go about
-compressing large language models such as BERT. Two alternatives stand out as
-particularly exciting possible future directions. \citet{liu2019multi} propose a
-method for complete weight sharing of BERT's encoder parameters across different
-tasks by simultaneously training for all tasks. We believe this approach could
-be relaxed through difference pruning to achieve a performance gain relative to
-each compression technique in isolation.
-
-\citet{frankle2018lottery} articulate in their ``lottery ticket hypothesis''
-that most networks contain sparse sub-networks which can perform similarly well.
-They provide an algorithm for finding these ``lottery tickets'' whose main
-differences to DeepTwist are (1) that weights that get distorted to 0 are permanently
-masked and kept at 0, and (2) that the algorithm progressively increases the
-pruning rate. This framework could serve as a competitive alternative to
-DeepTwist, and it would be interesting to see how it performs with difference
-pruning.
-
-\section*{Acknowledgements}
-
-We thank Alexander M. Rush and the Harvard CS 287 community, without whom
-this work would not have been possible.
-
-% TODO: thank Rush + 287
+% \section*{Acknowledgements}
 

### 2019-05-13 paper/paper.tex
Minor fixes

--- 2019-05-13 paper/paper.tex
@@
 computer vision tasks, though the drop in performance is less negligible.
-Knowledge distillation also achieves the compression objective with more
+Knowledge Distillation also achieves the compression objective with more
 sacrifices in  predictive accuracy.
@@
 A different framework, knowledge distillation, first proposed by 
-\citep{bucilua2006model} as
+\citet{bucilua2006model} as
 ``knowledge transfer,'' was recently popularized by
-\citep{hinton2015distilling}. In knowledge distillation, a simple network,
+\citet{hinton2015distilling}. In knowledge distillation, a simple network,
 called the \emph{student network}, is not trained on the actual data but on
@@
 the large model that performs well, termed the \emph{teacher network}, we
-train a smaller network $g$, the \emph{student network}, by minimizing,
+train a smaller network $g$, the \emph{student network}, by minimizing
 \[ \ell(g(\bm{x_i}), f(\bm{x_i})).\]
@@
 memory than then range of all possible $\btheta$s. For example, if $\btheta \in
-\mathbb{R}^{m,n}$, and the distortion produces a matrix of rank 1, then any
-distorted matrix could be uniquely identified by $\btheta' \in \mathbb{R}^{n+m}$
+\mathbb{R}^{m \times n}$, and the distortion produces a matrix of rank 1, then
+any
+distorted matrix could be uniquely identified by $\btheta' \in \mathbb{R}^{m+n}$
 through a matrix factorization.
@@
 \centering
-\includegraphics[width=.5\textwidth]{../figs/value_by_layer.pdf}
+\includegraphics[width=.48\textwidth]{../figs/value_by_layer.pdf}
 \caption{Weight distributions for five most/least variable layers}
@@
     \centering
-    \includegraphics[width=0.5\textwidth]
+    \includegraphics[width=0.46\textwidth]
     {../figs/svd-singular-vals-distribution.png}
@@
 normal curve from that point forward. We find this---depicted in
-\cref{fig:kdlstmloss}---remarkably puzzling. We hypothesize this may be the
+\cref{fig:kdlstmloss}---remarkably puzzling. We speculate this may be the
 effect of our adaptive learning rate starting out too low and taking multiple
